---
title: "Combined Cohort Analysis"
author: "Jason Giles"
date: "2023-06-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Creating environment for analysis of all 3 cohorts
## This files must be ran after the generation of the dataframes for the 3 cohorts

```{r}
library(tidyverse)
library(pscl)
library(MESS)
library(haven)
library(here)
library(psych)
library(skimr)
library(DataExplorer)
library(visdat)
library(mdscore)
library(oddsratio)
library(ppcor)
library(corrplot)
library(corrr)
library(readr)
library(tidyr)
library(ggplot2)
library(Hmisc)
library(RColorBrewer)
library(reshape2)
library(PupillometryR)
library(corrplot)
library(corrr)
library(MASS)
library(bestNormalize)
library(readxl)
library(car)
library(tableone)
library(olsrr)
library(MASS)
library(cutpointr)
library(car)
library(OptimalCutpoints)
library(lmtest)
library(pROC)
library(pastecs)

here()
```

### Merging the cohorts to make one unified dataframe
```{r}
greif_subset <- raw_greif_dataset %>% dplyr::select('ID', 'gender','age','IgG','HIPA_DK', 'OD_pos')
greif_subset$cohort <- 'greifswald'

greif_subset <- greif_subset %>% rename(functional_assay = 'HIPA_DK', OD = 'IgG')

mcmaster_subset <- raw_mcmaster_dataset %>% dplyr::select('new_abo','SEX','age','SRA','OD','OD_pos')
mcmaster_subset$cohort <- 'mcmaster'

mcmaster_subset <- mcmaster_subset %>% rename(ID = "new_abo",gender = "SEX", functional_assay = "SRA")

tours_subset <- raw_tours_dataset %>% dplyr::select("FID","age", "gender","OD","SRAnew2" ,"OD_pos")
tours_subset$cohort <- 'tours'

tours_subset <- tours_subset %>% rename(functional_assay = "SRAnew2", ID = "FID")


combined_subset <- bind_rows(greif_subset, tours_subset, mcmaster_subset)

dplyr::count(combined_subset, OD > 3)

```


### Rainbow plotting

```{r}
raincloud_theme = theme(
text = element_text(size = 10),
axis.title.x = element_text(size = 16),
axis.title.y = element_text(size = 16),
axis.text = element_text(size = 14),
axis.text.x = element_text(angle = 45, vjust = 0.5),
legend.title=element_text(size=16),
legend.text=element_text(size=16),
legend.position = "right",
plot.title = element_text(lineheight=.8, face="bold", size = 16),
panel.border = element_blank(),
panel.grid.minor = element_blank(),
panel.grid.major = element_blank(),
axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))

# Summary statsitics for the plots

lb <- function(x) mean(x) - sd(x)
ub <- function(x) mean(x) + sd(x)

```


### LEVENE test for homogeniety of variance
```{r}
# Test for antibody titer values across cohorts
leveneTest(combined_subset$OD, combined_subset$cohort)


# Test for age across cohorts
leveneTest(combined_subset$age, combined_subset$cohort)

## TESTING DIFFERENCES IN MCMASTER AND GREIFSWALD

# Test for antibody titer values across cohorts
leveneTest(combined_subset$OD[combined_subset$cohort != 'tours'], combined_subset$cohort[combined_subset$cohort != 'tours'])

# Test for age across cohorts
leveneTest(combined_subset$age[combined_subset$cohort != 'tours'], combined_subset$cohort[combined_subset$cohort != 'tours'])



## TESTING DIFFERENCES IN MCMASTER AND TOURS

# Test for antibody titer values across cohorts
leveneTest(combined_subset$OD[combined_subset$cohort != 'greifswald'], combined_subset$cohort[combined_subset$cohort != 'greifswald'])

# Test for age across cohorts
leveneTest(combined_subset$age[combined_subset$cohort != 'greifswald'], combined_subset$cohort[combined_subset$cohort != 'greifswald'])


## TESTING DIFFERENCES IN GREIFSWALD AND TOURS

# Test for antibody titer values across cohorts
leveneTest(combined_subset$OD[combined_subset$cohort != 'mcmaster'], combined_subset$cohort[combined_subset$cohort != 'mcmaster'])

# Test for age across cohorts
leveneTest(combined_subset$age[combined_subset$cohort != 'mcmaster'], combined_subset$cohort[combined_subset$cohort != 'mcmaster'])

```


### Test if Age and OD is normally distributed
```{r}
# McMaster Cohort
shapiro.test(combined_subset$OD[combined_subset$cohort == 'mcmaster'])
qqnorm(combined_subset$OD[combined_subset$cohort == 'mcmaster'])
qqline(combined_subset$OD[combined_subset$cohort == 'mcmaster'])

# Greifswald Cohort
shapiro.test(combined_subset$OD[combined_subset$cohort == 'greifswald'])
qqnorm(combined_subset$OD[combined_subset$cohort == 'greifswald'])
qqline(combined_subset$OD[combined_subset$cohort == 'greifswald'])

# Tours Cohort
shapiro.test(combined_subset$OD[combined_subset$cohort == 'tours'])
qqnorm(combined_subset$OD[combined_subset$cohort == 'tours'])
qqline(combined_subset$OD[combined_subset$cohort == 'tours'])

```

### Data is non-parametric: Must use a non-parametric homogeneity test

```{r}
# Perform the Fligner-Killeen test
result <- fligner.test(combined_subset$OD ~ combined_subset$cohort, combined_subset)

# Print the test result
print(result)

# Test on McMaster vs Greifswald 

result <- fligner.test(combined_subset$OD[combined_subset$cohort != 'tours'], combined_subset$cohort[combined_subset$cohort != 'tours'])

# Print the test result
print(result)

# age variance test 
result <- fligner.test(combined_subset$age ~ combined_subset$cohort, combined_subset)

# Print the test result
print(result)

# Age mcmaster vs greifswald
result <- fligner.test(combined_subset$age[combined_subset$cohort != 'tours'], combined_subset$cohort[combined_subset$cohort != 'tours'])

# Print the test result
print(result)


# Age tours vs greifswald
result <- fligner.test(combined_subset$age[combined_subset$cohort != 'mcmaster'], combined_subset$cohort[combined_subset$cohort != 'mcmaster'])

# Print the test result
print(result)

# Age tours vs mcmaster
result <- fligner.test(combined_subset$age[combined_subset$cohort != 'greifswald'], combined_subset$cohort[combined_subset$cohort != 'greifswald'])

# Print the test result
print(result)
```

### Testing of boot.heterogeneity package
```{r}
confint(gender_HIT_hetero)

# Effect sizes and SE accross 3 cohorts for OD ~ HIT: Greif, Tours, McMaster

yi <- c(2.73923,2.9976,3.9481)
sei <- c(0.08337,0.2202, 0.1758)
di <- c(1,2,3)
# Random effects model for heterogeneity
OD_HIT_hetero <- rma(yi = yi, sei = sei, method = 'REML', measure = 'OR', digits = 16)
OD_HIT_hetero

confint(OD_HIT_hetero)

```

### Coefficient of variation analysis
```{r}


# Create an empty vector to store the cov values
cov <- numeric(nrow(raw_mcmaster_dataset))

raw_mcmaster_dataset$cov <- NA
raw_mcmaster_dataset$cov_per <- NA

# Loop through each row in the dataframe
for (i in 1:nrow(raw_mcmaster_dataset)) {
  # Calculate the mean for the row
  row_mean <- mean(c(raw_mcmaster_dataset$IgG[i], raw_mcmaster_dataset$IgP[i]))

  # Calculate the standard deviation for the row
  row_sd <- sd(c(raw_mcmaster_dataset$IgG[i], raw_mcmaster_dataset$IgP[i]))

  # Calculate the coefficient of variation (cov)
  row_cov <- row_sd / row_mean

  # Assign the cov value to the corresponding index in the "cov" vector
  raw_mcmaster_dataset$cov[i] <- row_cov
  
  # assign the cov to a percentage
  raw_mcmaster_dataset$cov_per[i] <- row_cov*100
}

# Print the "cov" values
print(raw_mcmaster_dataset$cov)
print(raw_mcmaster_dataset$cov_per)
mean(raw_mcmaster_dataset$cov, na.rm = T)
dplyr:: count(raw_mcmaster_dataset, is.na(cov))
min(raw_mcmaster_dataset$cov, na.rm = T)
max(raw_mcmaster_dataset$cov, na.rm = T)

dplyr:: count(raw_mcmaster_dataset, cov < .30)

filter(raw_mcmaster_dataset, SRA == 1) %>% count(cov_per < 30)

ggplot(raw_mcmaster_dataset, aes(x= cov)) +
  geom_histogram(bins = 100, colour="black", fill="white")+
  geom_density(alpha=.2, fill="#FF6666") +
  labs(x = "Covariance value", y = "Count") +
  ggtitle("Plot of Covariate Values") +
  geom_vline(aes(xintercept=0.35),
            color="blue", linetype="dashed", size=1)







# Publication quality 

# Subset the data
subset_data <- subset(raw_mcmaster_dataset, !is.na(SRA))

# Set theme options for publication quality
theme_set(theme_bw())
theme_update(plot.title = element_text(size = 16, face = "bold"),
             axis.title = element_text(size = 14),
             axis.text = element_text(size = 12),
             legend.title = element_text(size = 12),
             legend.text = element_text(size = 12))

# Create the plot

ggplot(subset_data, aes(x = cov, fill = SRA)) +
  geom_histogram(bins = 100, colour = "black") +
  geom_density(alpha = 0.6, fill = "#F9F7C5") +
  labs(x = "Coefficient of Variation", y = "Count") +
  ggtitle("") +
  geom_vline(aes(xintercept = 0.35), color = "blue", linetype = "dashed", size = 1) +
  guides(fill = guide_legend(title = "SRA Group")) +
  scale_fill_discrete(labels=c('Negative', 'Positive')) + 
  theme(legend.position = "right")


ggplot(subset_data, aes(x = cov, fill = SRA)) +
  geom_histogram(bins = 100, colour = "black") +
  geom_density(alpha = 0.6, fill = "#F9F7C5") +
  labs(x = "Coefficient of Variance", y = "Count") +
  ggtitle("") +
  geom_vline(aes(xintercept = 0.35), color = "blue", linetype = "dashed", size = 1) +
  guides(fill = guide_legend(title = "Functional \nAssay")) +
  scale_fill_manual(values = c("salmon", "red4"), labels=c('Negative', 'Positive')) +
  theme(legend.position = "right",
        panel.grid = element_blank(),
        plot.margin = margin(1, 1, 1, 1, "cm"),
        axis.line = element_line(colour = "black"),
        panel.border = element_rect(colour = "black", fill = NA))

# REmove the line from the graph
ggplot(subset_data, aes(x = cov, fill = SRA)) +
  geom_histogram(bins = 100, colour = "black") +
  labs(x = "Coefficient of Variation", y = "Count") +
  ggtitle("") +
  guides(fill = guide_legend(title = "Functional \nAssay")) +
  scale_fill_manual(values = c("salmon", "red4"), labels=c('Negative', 'Positive')) +
  theme(legend.position = "right") +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())

# Save the plot as a publication-quality image
ggsave(here("../Figures/Figure_COV_06_09_23.jpeg"),plot = last_plot(), width = 7, height = 7, units = 'in' , dpi = 600)

# Figure 2B
```


### Spearman correlation Coefficient
```{r}

cor_result <- cor.test(raw_mcmaster_dataset$IgG, raw_mcmaster_dataset$IgP, type = "spearman")
cor_result
cor_value <- cor_result$estimate
cor_value

p_value <- cor_result$p.value
p_value


ggplot(raw_mcmaster_dataset, aes(x = IgG, y = IgP)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(x = "IgG", y = "IgP") +
  ggtitle("Scatter Plot with Trendline and Confidence Intervals") +
  geom_text(x = Inf, y = -Inf, label = paste("Spearman's rho =", round(cor_value, 3), "p =", cor_result$p.value),
            hjust = 1.5, vjust = -2, size = 4, color = "blue")

ggplot(raw_mcmaster_dataset, aes(x = IgG, y = IgP)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  coord_cartesian(xlim = c(0,4.5), ylim = c(0,4.5)) +
  labs(x = "IgG", y = "IgP") +
  ggtitle("Scatter Plot with Trendline and Confidence Intervals") +
  geom_text(x = Inf, y = -Inf, label = paste("Spearman's rho =", round(cor_value, 3), "p =", cor_result$p.value),
            hjust = 1.5, vjust = -2, size = 4, color = "blue")


ggplot(raw_mcmaster_dataset, aes(x = IgG, y = IgP)) +
  geom_point() +
  geom_smooth(method = "loess", se = TRUE) +
  coord_cartesian(xlim = c(0,4.5), ylim = c(0,4.5)) +
  labs(x = "IgG", y = "IgP") +
  ggtitle("Scatter Plot with Trendline and Confidence Intervals") +
  geom_text(x = Inf, y = -Inf, label = paste("Spearman's rho =", round(cor_value, 3), "p =", cor_result$p.value),
            hjust = 1.5, vjust = -2, size = 4, color = "blue")

#---------------------- subsetting/ grouping by SRA status


       
ggplot(subset(raw_mcmaster_dataset, !is.na(SRA)), aes(x = IgG, y = IgP)) +
  geom_point(color='black', shape=21, size=4, aes(fill=factor(SRA))) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(x = "Monoclonal ELISA (IgG)", y = "Polyclonal ELISA (IgA/G/M)") +
  ggtitle("") +
  guides(fill = guide_legend(title = "Functional \nAssay")) +
  scale_fill_manual(values = c("salmon", "red4"), labels=c('Negative', 'Positive')) +
  geom_text(x = Inf, y = -Inf, label = paste0("Rho = ", round(cor_value, 3), ", P < 2.2e-16 "),
            hjust = 2, vjust = -35, size = 6, color = "black", parse = F) +
  theme(panel.background = element_blank())


  
ggsave(here("../Figures/Figure_igg_v_igp_06_05_23.jpeg"), plot = last_plot(), width = 7, height = 7, units = 'in' , dpi = 600)

#Figure 2A
```

### Correlation coefficent with Greifswald IgA with IgG
```{r}
greif_neg_od_rm <- filter(raw_greif_dataset, IgG > 0, IgA > 0)

cor_result_greif_igg_iga <- cor.test(greif_neg_od_rm$IgG, greif_neg_od_rm$IgA, type = "spearman")
cor_result_greif_igg_iga

cor_value_greif_igg_iga <- cor_result_greif_igg_iga$estimate
cor_value_greif_igg_iga

cor_p_value_greif_igg_iga <- cor_result_greif_igg_iga$p.value
cor_p_value_greif_igg_iga


ggplot(greif_neg_od_rm, aes(x = IgG, y = IgA)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(x = "IgG", y = "IgA") +
  ggtitle("Scatter Plot of IgA and IgG with Trendline and Confidence Intervals") +
  geom_text(x = Inf, y = -Inf, label = paste("Spearman's rho =", round(cor_value_greif_igg_iga, 3), "p =", cor_result_greif_igg_iga$p.value),
            hjust = 1.5, vjust = -28, size = 4, color = "blue")


ggplot(greif_neg_od_rm, aes(x = IgG, y = IgA)) +
  geom_point() +
  geom_smooth(method = "loess", se = TRUE) +
  labs(x = "IgG", y = "IgA") +
  ggtitle("Scatter Plot of IgA and IgG with Trendline and Confidence Intervals") +
  geom_text(x = Inf, y = -Inf, label = paste("Spearman's rho =", round(cor_value_greif_igg_iga, 3), "p =", cor_result_greif_igg_iga$p.value),
            hjust = 1.5, vjust = -28, size = 4, color = "blue")

#--------------------------------------- subsetting by HIPA status

ggplot(subset(greif_neg_od_rm, !is.na(HIPA_DK)), aes(x = IgG, y = IgA)) +
  geom_point(color='black', shape=21, size=2, aes(fill=factor(HIPA_DK))) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(x = "IgG", y = "IgA") +
  ggtitle("") +
  guides(fill = guide_legend(title = "Functional \nAssay")) +
  scale_fill_manual(values = c("salmon", "red4"), labels=c('Negative', 'Positive')) +
  geom_text(x = Inf, y = -Inf, label = paste0("Rho = ", round(cor_value_greif_igg_iga, 3), ", P < 2.2e-16"),
            hjust = 1.9, vjust = -35, size = 6, color = "black") +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())


# Save the plot as a publication-quality image
ggsave(here("../Figures/Figure_igg_v_iga_06_05_23.jpeg"),plot = last_plot(), width = 7, height = 7, units = 'in' , dpi = 600)
#Figure 2C
```

### Correlation coefficent with Greifswald Igm  with IgG
```{r}


cor_result_greif_igg_IgM <- cor.test(greif_neg_od_rm$IgG, greif_neg_od_rm$IgM, type = "spearman")
cor_result_greif_igg_IgM
cor_value_greif_igg_IgM <- cor_result_greif_igg_IgM$estimate
cor_value_greif_igg_IgM

cor_p_value_greif_igg_IgM <- cor_result_greif_igg_IgM$p.value
cor_p_value_greif_igg_IgM


ggplot(greif_neg_od_rm, aes(x = IgG, y = IgM)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(x = "IgG", y = "IgM") +
  ggtitle("Scatter Plot of IgM and IgG with Trendline and Confidence Intervals") +
  geom_text(x = Inf, y = -Inf, label = paste("Spearman's rho =", round(cor_value_greif_igg_IgM, 3), "p =", cor_result_greif_igg_IgM$p.value),
            hjust = 1.5, vjust = -28, size = 4, color = "blue")


ggplot(greif_neg_od_rm, aes(x = IgG, y = IgM)) +
  geom_point() +
  geom_smooth(method = "loess", se = TRUE) +
  labs(x = "IgG", y = "IgM") +
  ggtitle("Scatter Plot of IgM and IgG with Trendline and Confidence Intervals") +
  geom_text(x = Inf, y = -Inf, label = paste("Spearman's rho =", round(cor_value_greif_igg_IgM, 3), "p =", cor_result_greif_igg_IgM$p.value),
            hjust = 1.5, vjust = -40, size = 4, color = "blue")


#--------------------------------------- subsetting by HIPA status

ggplot(subset(greif_neg_od_rm, !is.na(HIPA_DK)), aes(x = IgG, y = IgM)) +
  geom_point(color='black', shape=21, size=2, aes(fill=factor(HIPA_DK))) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(x = "IgG", y = "IgM") +
  ggtitle("Scatter Plot of IgM and IgG with Trendline and Confidence Intervals") +
  geom_text(x = Inf, y = -Inf, label = paste("Spearman's rho =", round(cor_value_greif_igg_IgM, 3), "p =", cor_result_greif_igg_IgM$p.value),
            hjust = 1.5, vjust = -28, size = 4, color = "blue")


ggplot(subset(greif_neg_od_rm, !is.na(HIPA_DK)), aes(x = IgG, y = IgM)) +
  geom_point(color='black', shape=21, size=2, aes(fill=factor(HIPA_DK))) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(x = "IgG", y = "IgM") +
  ggtitle("") +
  guides(fill = guide_legend(title = "Functional \nAssay")) +
  scale_fill_manual(values = c("salmon", "red4"), labels=c('Negative', 'Positive')) +
  geom_text(x = Inf, y = -Inf, label = paste0("Rho = ", round(cor_value_greif_igg_IgM, 3), ", P < 2.2e-16"),
            hjust = 1.9, vjust = -35, size = 6, color = "black") +
  theme(panel.background = element_blank(),
        panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        panel.border = element_blank())


# Save the plot as a publication-quality image
ggsave(here("../Figures/Figure_igg_v_igm_06_05_23.jpeg"),plot = last_plot(), width = 7, height = 7, units = 'in' , dpi = 600)
# FIgure 2D
```


### Correlation coefficent with Greifswald Igm  with IgA
```{r}


cor_result_greif_igg_iga <- cor.test(greif_neg_od_rm$IgA, greif_neg_od_rm$IgM, type = "spearman")
cor_result_greif_igg_iga
cor_value_greif_igg_iga <- cor_result_greif_igg_iga$estimate
cor_value_greif_igg_iga

cor_p_value_greif_igg_iga <- cor_result_greif_igg_iga$p.value
cor_p_value_greif_igg_iga


ggplot(greif_neg_od_rm, aes(x = IgA, y = IgM)) +
  geom_point() +
  geom_smooth(method = "lm", se = TRUE) +
  labs(x = "IgA", y = "IgM") +
  ggtitle("Scatter Plot of IgA and IgM with Trendline and Confidence Intervals") +
  geom_text(x = Inf, y = -Inf, label = paste("Spearman's rho =", round(cor_value_greif_igg_IgM, 3), "p =", cor_result_greif_igg_IgM$p.value),
            hjust = 1.5, vjust = -28, size = 4, color = "blue")


ggplot(greif_neg_od_rm, aes(x = IgA, y = IgM)) +
  geom_point() +
  geom_smooth(method = "loess", se = TRUE) +
  labs(x = "IgA", y = "IgM") +
  ggtitle("Scatter Plot of IgA and IgM with Trendline and Confidence Intervals") +
  geom_text(x = Inf, y = -Inf, label = paste("Spearman's rho =", round(cor_value_greif_igg_IgM, 3), "p =", cor_result_greif_igg_IgM$p.value),
            hjust = 1.5, vjust = -28, size = 4, color = "blue")


#--------------------------------------- subsetting by HIPA status

ggplot(subset(greif_neg_od_rm, !is.na(HIPA_DK)), aes(x = IgA, y = IgM)) +
  geom_point(color='black', shape=21, size=2, aes(fill=factor(HIPA_DK))) +
  geom_smooth(method = "lm", se = TRUE) +
  labs(x = "IgA", y = "IgM") +
  ggtitle("Scatter Plot of IgM and IgA with Trendline and Confidence Intervals") +
  geom_text(x = Inf, y = -Inf, label = paste("Spearman's rho =", round(cor_value_greif_igg_IgM, 3), "p =", cor_result_greif_igg_IgM$p.value),
            hjust = 1.5, vjust = -28, size = 4, color = "blue")
```
# Correlation coefficent with McMaster IgG  with IgP
```{r}
raw_mcmaster_na_rm_od <- raw_mcmaster_dataset %>% drop_na(OD)

cor_result_mcmaster_igg_igp <- cor.test(raw_mcmaster_na_rm_od$IgP, raw_mcmaster_na_rm_od$IgG, type = "spearman")
cor_result_mcmaster_igg_igp
cor_value_mcmcaster_igg_igp <- cor_result_mcmaster_igg_igp$estimate
cor_value_mcmcaster_igg_igp

cor_p_value_mcmaster_igg_igp <- cor_result_mcmaster_igg_igp$p.value
cor_p_value_mcmaster_igg_igp


```

# Figures and Tables
## Table 1

```{r}

# Just table on on McMaster
varss_mcmaster <- c("age", "SEX", "OD","SRA", "GROUP", "RH","Surgery_Patient", "O_type", "OD_pos")
cat_varss_mcmaster <- c("SEX", "SRA", "GROUP","RH", "Surgery_Patient", 'O_type', 'OD_pos')

raw_mcmaster_od_miss_rm <- filter(raw_mcmaster_dataset, !is.na(OD))

tab1_mcmaster <- CreateTableOne(vars = varss_mcmaster, data = raw_mcmaster_od_miss_rm, factorVars = cat_varss_mcmaster, includeNA = F)
tab1_mcmaster


### TOURS

varss <- c("age", "gender", "OD","SRAnew2", "UFH", "PLT_before","CPBnew", 'OD_pos')
cat_varss <- c("gender", "SRAnew2", "UFH","CPBnew", 'OD_pos')

tours_demographic_od_miss_rm <- filter(raw_tours_dataset, !is.na(OD))


tab1 <- CreateTableOne(vars = varss, data = tours_demographic_od_miss_rm, factorVars = cat_varss, includeNA = F)
tab1

# Greifswald

varss <- c("age", "gender", "IgG","IgA", 'IgM', "HIPA_DK", "OD_pos")
cat_varss <- c("gender", "HIPA_DK", "OD_pos")

raw_greif_dataset_od_miss_rm <- filter(raw_greif_dataset, !is.na(IgG))

tab1_greif <- CreateTableOne(vars = varss, data = raw_greif_dataset_od_miss_rm, factorVars = cat_varss)
tab1_greif




#---------------------

# combined Table 1 

varss <- c('gender','age','OD','OD_pos','functional_assay','cohort')
cat_varss <- c('gender','OD_pos', 'functional_assay','cohort')

tab1_all <- CreateTableOne(vars = varss, data = combined_subset, factorVars = cat_varss, strata = 'cohort', includeNA = F, testNonNormal = T)

tab1_all
```

## Figure 1 - Distribution of IgG titers across cases and controls

### McMaster
```{r}

dplyr::count(raw_mcmaster_dataset, is.na(OD))


k <- ggplot(data = subset(raw_mcmaster_dataset, !is.na(SRA)), aes(y = OD, x = SRA, fill = SRA)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
geom_point(aes(y = OD, color = SRA), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
geom_boxplot(width = .1, show.legend = FALSE, outlier.shape = NA, alpha = 0.5) +
expand_limits(x = 2) +
guides(color = "none", fill = 'none') +
scale_fill_manual(values = c("salmon", "red4"), labels=c('Negative', 'Positive')) +
scale_color_manual(values = c("salmon", "red4"), labels=c('Negative', 'Positive')) +
coord_flip() +
theme_bw() +
raincloud_theme

k

k + labs(y = 'Anti-PF4/heparin Antibody Optical Density', x = NULL, title = '') + scale_x_discrete(labels = c('Negative', 'Positive')) + scale_y_continuous(breaks = round(seq(0, 5, by = 0.5),2), limits = c(0,4.5)) + theme(axis.title.x = element_text(size = 10)) 

ggsave(here('../Figures/McMaster_figure1_06_05_23.jpeg'), plot = last_plot(),  dpi = 600, width = 6, height = 4)
```


## Tours
```{r}
dplyr::count(raw_tours_dataset, is.na(OD))

l <- ggplot(data = subset(raw_tours_dataset, !is.na(SRAnew2)), aes(y = OD, x = SRAnew2, fill = SRAnew2)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
geom_point(aes(y = OD, color = SRAnew2), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
geom_boxplot(width = .1, show.legend = FALSE, outlier.shape = NA, alpha = 0.5) +
expand_limits(x = 2) +
guides(color = "none", fill = 'none') +
scale_fill_manual(values = c("salmon", "red4"), labels=c('Negative', 'Positive')) +
scale_color_manual(values = c("salmon", "red4"), labels=c('Negative', 'Positive')) +
coord_flip() +
theme_bw() +
raincloud_theme


l + labs(y = 'Anti-PF4/heparin Antibody Optical Density', x = NULL, title = '') + scale_x_discrete(labels = c('Negative', 'Positive')) + scale_y_continuous(breaks = round(seq(0, 5, by = 0.5),2), limits = c(0,4.5)) + theme(axis.title.x = element_text(size = 10))

ggsave(here('../Figures/Tours_figure1_06_05_23.jpeg'), plot = last_plot(),
       dpi = 600, width = 6, height = 4)
```

### Greifswald
```{r}
dplyr::count(raw_greif_dataset, is.na(IgG))


m <- ggplot(data = subset(raw_greif_dataset, !is.na(HIPA_DK) & IgG > 0), aes(y = IgG, x = HIPA_DK, fill = HIPA_DK)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
geom_point(aes(y = IgG, color = HIPA_DK), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
geom_boxplot(width = .1, show.legend = FALSE, outlier.shape = NA, alpha = 0.5) +
expand_limits(x = 2) +
guides(color = "none", fill = 'none') +
scale_fill_manual(values = c("salmon", "red4"), labels=c('Negative', 'Positive')) +
scale_color_manual(values = c("salmon", "red4"), labels=c('Negative', 'Positive')) +
coord_flip() +
theme_bw() +
raincloud_theme

m


m + labs(y = 'Anti-PF4/heparin Antibody Optical Density', x = NULL, title = '') + scale_x_discrete(labels = c('Negative', 'Positive')) + scale_y_continuous(breaks = round(seq(0, 5, by = 0.5),2), limits = c(0,4.5)) + theme(axis.title.x = element_text(size = 10))

ggsave(here('../Figures/Greif_figure1_06_05_23.jpeg'), plot = last_plot(),
       dpi = 600, width = 6, height = 4)

```


# Figure 4 - Cutpoint of antibody prediction model
```{r}

tours_optimal_cut_df <- raw_tours_dataset %>% dplyr::select(predictor = OD, outcome = SRAnew2) %>% mutate(cohort = 'Tours')

mcmaster_optimal_cut_df <- raw_mcmaster_dataset %>% dplyr::select(predictor = OD, outcome = SRA) %>% mutate(cohort = 'McMaster')

greif_optimal_cut_df <- raw_greif_dataset %>% dplyr::select(predictor = IgG, outcome = HIPA_DK) %>% mutate(cohort = 'Greifswald')

combined_optimal_cut_df <- rbind(mcmaster_optimal_cut_df, tours_optimal_cut_df, greif_optimal_cut_df)

combined_optimal_cut_df$cohort <- factor(combined_optimal_cut_df$cohort, levels = c("Tours",'McMaster',"Greifswald"))

combined_optimal_cut_df <- subset(combined_optimal_cut_df, predictor > 0)
cut_youdens_combined <- cutpointr(combined_optimal_cut_df, predictor, outcome, subgroup = cohort, method = maximize_metric, metric = youden, na.rm = T)

summary(cut_youdens_combined)
plot_roc(cut_youdens_combined)

plts <- plot_metric(cut_youdens_combined)
plts

plts + ggtitle('', subtitle = '') + theme_classic() + labs(x = 'Antibody Level [OD]', y = "Youden's J", color = 'Cohort') +
  scale_x_continuous(breaks = round(seq(0, max((combined_optimal_cut_df$predictor +0.1), na.rm = T), by = 0.5),1))

plts + ggtitle('', subtitle = '') + theme_classic() + labs(x = 'Antibody Level [OD]', y = "Youden's J", color = 'Cohort') +
  scale_x_continuous(breaks = round(seq(0, max((combined_optimal_cut_df$predictor +0.1), na.rm = T), by = 0.5),1)) +
  scale_color_manual(values = c("Greifswald" = "red4", "McMaster" = "seagreen",  "Tours" =  'mediumblue'))

ggsave(here("../Figures/Figure4_06_05_23.jpeg"), dpi = 600, height = 7, width = 7, units = 'in')


```

### Combining all three cohorts for total youden's J
```{r}


#combined_optimal_cut_df <- rbind(McMaster_df, tours_df, greif_optimal_cut_df)
?cutpointr
cut_youdens_combined <- cutpointr(combined_optimal_cut_df, predictor, outcome, method = maximize_metric, metric = youden, na.rm = T)

summary(cut_youdens_combined)

plts <- plot_metric(cut_youdens_combined)
plts + ggtitle('', subtitle = '') +theme_classic() + labs(x = 'Antibody Level [OD]', y = "Youden's J", color = 'Cohort')


# Manual combined cohort cutopints 

cut_youdens_combined <- cutpointr(combined_optimal_cut_df, predictor, outcome, method = oc_manual, cutpoint = 0.4, na.rm = T)

summary(cut_youdens_combined)

cut_youdens_combined <- cutpointr(combined_optimal_cut_df, predictor, outcome, method = oc_manual, cutpoint = 2.0, na.rm = T)

summary(cut_youdens_combined)
```



# Figure 4B - Cutpoint of stepwise regression model
```{r}
# making dataframe without missing data
tours_demographic_naomit <- filter(raw_tours_dataset, !is.na(OD) & !is.na(gender) & !is.na(SRAnew2))

stepwise_tours <- glm(data = tours_demographic_naomit, SRAnew2 ~ OD + gender, family = binomial(link = 'logit') )

coef(stepwise_tours)

tours_demographic_naomit$predictor_stepwise <- predict(stepwise_tours)
tours_demographic_naomit$outcome_stepwise <- tours_demographic_naomit$SRAnew2

tours_df <- tours_demographic_naomit %>% dplyr::select(predictor_stepwise, outcome_stepwise) %>% mutate(cohort = 'Tours')


# Greifswald cohort
raw_greif_naomit <- filter(raw_greif_dataset, !is.na(IgG) & !is.na(gender) & !is.na(HIPA_DK))

stepwise_greif <- glm(data = raw_greif_naomit, HIPA_DK ~ IgG + gender, family = binomial(link = 'logit'))
coef(stepwise_greif)

raw_greif_naomit$predictor_stepwise <- predict(stepwise_greif)
raw_greif_naomit$outcome_stepwise <- raw_greif_naomit$HIPA_DK

greif_df <- raw_greif_naomit %>% dplyr::select(predictor_stepwise, outcome_stepwise) %>% mutate(cohort = 'Greifswald')

# McMaster Cohort

raw_mcmaster_naomit <- filter(raw_mcmaster_dataset, !is.na(OD) & !is.na(SEX) & !is.na(SRA))

stepwise_mcmaster <- glm(data = raw_mcmaster_naomit, SRA ~ OD + SEX, family = binomial(link = 'logit') )

coef(stepwise_mcmaster)

raw_mcmaster_naomit$predictor_stepwise <- predict(stepwise_mcmaster)
raw_mcmaster_naomit$outcome_stepwise <- raw_mcmaster_naomit$SRA

McMaster_df <- raw_mcmaster_naomit %>% dplyr::select(predictor_stepwise, outcome_stepwise) %>% mutate(cohort = 'McMaster')

# Combining the datasets

stepwise_model_combined_df <- rbind(tours_df, greif_df, McMaster_df)

stepwise_model_combined_df_cut_youdens <- cutpointr(stepwise_model_combined_df, predictor_stepwise, outcome_stepwise,cohort, method = maximize_metric, metric = youden, na.rm = T)

summary(stepwise_model_combined_df_cut_youdens)



# PLOT AUC CURVE 


roc_plt <- plot_roc(stepwise_model_combined_df_cut_youdens)
roc_plt
roc_plt + ggtitle('', subtitle = '') + theme_classic() + scale_color_manual(values = c(c("Greifswald" = "red4", "McMaster" = "seagreen",  "Tours" =  'mediumblue'))) + labs(color = 'Cohort') + geom_line(size = 1.5)  

ggsave(here("../Figures/Figure4roc_stepwise_06_06_23.jpeg"), dpi = 600, height = 7, width = 7, units = 'in')




```

### Figure 3 Sankey image

```{r}
#devtools::install_github("davidsjoberg/ggsankey")
library(ggsankey)
library(dplyr)

# Mcmaster dataframe generation
data <- data.frame(Total = c(rep('Total',2720)), 
                   Prediction = c(rep("Positive", 492), rep("Negative", 2228)),
                   Results = c(rep("True Pos",338),rep("False Pos", 154), rep("False Neg", 10), rep('True Neg', 2218)))
df <- data %>%
  make_long(Total,Prediction,Results)

df_nr <- 
  df %>% 
  filter(!is.na(node)) %>% 
  group_by(x, node)%>% 
  dplyr::summarise(count = n())


# join to sankey dataframe

df <- 
  df %>% 
  left_join(df_nr)



#detach('package:plyr')
# attempt 1


n <- ggplot(df, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               label = node)) +
  geom_sankey(flow.alpha = 0.5, node.color = 1) +
  geom_sankey_label(aes(label = paste(node,count, sep = '=')), size = 4, color = 1, fill = "white") +
  #geom_sankey_text(aes(label = count), size = 3.5, vjust = -1, hjust = -1.50, check_overlap = T) +
  scale_fill_viridis_d(option = "A", alpha = 0.95)  +
  theme_sankey(base_size = 20) +  theme(legend.position = 'none') + labs(title = "McMaster Cohort") +
  theme(plot.title = element_text(hjust = 0.5 , vjust = -7)) + theme(axis.title.x=element_blank(), axis.title.y = element_blank()) + annotate("text", x = 2, y = 800, label = "Youden's J = 0.906", size = 4) + theme(plot.title = element_text(size=20))

n

ggsave(here("../Figures/Figure3_McMaster.jpeg"), plot = n, width = 7, height = 7, units = 'in' , dpi = 600)

ggsave(here("../Figures/Figure3_McMaster_2.jpeg"), plot = n, dpi = 600 )


# Tours

data <- data.frame(Total = c(rep('Total',828)), 
                   Prediction = c(rep("Positive", 273), rep("Negative", 555)),
                   Results = c(rep("True Pos",184),rep("False Pos", 89), rep("False Neg", 7), rep('True Neg', 548)))
df <- data %>%
  make_long(Total,Prediction,Results)

df_nr <- 
  df %>% 
  filter(!is.na(node)) %>% 
  group_by(x, node)%>% 
  dplyr::summarise(count = n())
#> `summarise()` has grouped output by 'x'. You can override using the `.groups` argument.

# join to sankey dataframe

df <- 
  df %>% 
  left_join(df_nr)



#detach('package:plyr')
# attempt 1


o <- ggplot(df, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               label = node)) +
  geom_sankey(flow.alpha = 0.5, node.color = 1) +
  geom_sankey_label(aes(label = paste(node,count, sep = '=')), size = 4, color = 1, fill = "white") +
  #geom_sankey_text(aes(label = count), size = 3.5, vjust = -1, hjust = -1.50, check_overlap = T) +
  scale_fill_viridis_d(option = "A", alpha = 0.95) +
  theme_sankey(base_size = 20) +  theme(legend.position = 'none') + labs(title = "Tours Cohort") + annotate("text", x = 2, y = 150, label = "Youden's J = 0.824", size = 4) +
  theme(plot.title = element_text(hjust = 0.5, vjust = -7)) + theme(axis.title.x=element_blank(), axis.title.y = element_blank()) + theme(plot.subtitle = element_text(hjust = 0.5))+ theme(plot.caption = element_text(hjust = 0.5)) + theme(plot.title = element_text(size=20))

o


ggsave(here("../Figures/Figure3_Tours.jpeg"), width = 4400, height = 2714, units = 'px' , plot = o)

ggsave(here("../Figures/Figure3_Tours_2.jpeg"), dpi = 600, plot = o )



# Greifswald

data <- data.frame(Total = c(rep('Total',4500)), 
                   Prediction = c(rep("Positive", 1453), rep("Negative", 3047)),
                   Results = c(rep("True Pos",983),rep("False Pos", 470), rep("False Neg", 219), rep('True Neg', 2828)))
df <- data %>%
  make_long(Total,Prediction,Results)

df_nr <- 
  df %>% 
  filter(!is.na(node)) %>% 
  group_by(x, node)%>% 
  dplyr::summarise(count = n())
#> `summarise()` has grouped output by 'x'. You can override using the `.groups` argument.

# join to sankey dataframe

df <- 
  df %>% 
  left_join(df_nr)


p <- ggplot(df, aes(x = x, 
               next_x = next_x, 
               node = node, 
               next_node = next_node,
               fill = factor(node),
               label = node)) +
  geom_sankey(flow.alpha = 0.5, node.color = 1) +
  geom_sankey_label(aes(label = paste(node,count, sep = '=')), size = 4, color = 1, fill = "white") +
  #geom_sankey_text(aes(label = count), size = 3.5, vjust = -1, hjust = -1.50, check_overlap = T) +
  scale_fill_viridis_d(option = "A", alpha = 0.95) +
  theme_sankey(base_size = 20) +  theme(legend.position = 'none') + labs(title = "Greifswald Cohort") +
  theme(plot.title = element_text(hjust = 0.5, vjust = -7)) + theme(axis.title.x=element_blank(), axis.title.y=element_blank()) + 
  annotate("text", x = 2, y = 750, label = "Youden's J = 0.675", size = 4) + theme(plot.title = element_text(size=20))

p


ggsave(here("../Figures/Figure5_Greifswald.jpeg"), dpi = 600)

```


