---
title: "Greifswald Demographic Analysis"
author: "Jason Giles"
date: "2023-06-23"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Install packages and read in data
```{r}
library(pscl)
library(tidyverse)
library(MESS)
library(haven)
library(here)
library(psych)
library(skimr)
library(DataExplorer)
library(visdat)
library(mdscore)
library(oddsratio)
library(ppcor)
library(corrplot)
library(corrr)
library(readr)
library(tidyr)
library(ggplot2)
library(Hmisc)
library(RColorBrewer)
library(reshape2)
library(PupillometryR)
library(corrplot)
library(corrr)
library(MASS)
library(bestNormalize)
library(readxl)
library(car)
library(tableone)
library(olsrr)
library(MASS)
library(cutpointr)
library(car)
library(OptimalCutpoints)
library(lmtest)
library(pROC)
library(pastecs)
library(dplyr)
library(here)

here()

# Reading in the Demographic data
raw_greif_dataset <- readxl::read_excel(here('../Final data base Greifswald patients GWA HIT STUDY_20161215.xlsx'), sheet = 2)

# Removing all individuals less that 18 years old
raw_greif_dataset <- raw_greif_dataset %>% filter(raw_greif_dataset$age > 18)
```

### Exploration of the data & summary 

```{r}
skim(raw_greif_dataset)
summary(raw_greif_dataset)

# recoding HIT assessment to be a factor level variable
raw_greif_dataset$final_HIT_Assessment <- as.factor(raw_greif_dataset$final_HIT_Assessment)

skim(raw_greif_dataset)

# visualizing the overall data structure
vis_miss(raw_greif_dataset)
vis_dat(raw_greif_dataset)

```

### Coding HIPA varaibles based on the HIPA_assessment variable

```{r}

## recode for HIPA_DK
raw_greif_dataset$HIPA_DK <- 0

raw_greif_dataset$HIPA_DK <- na_if(raw_greif_dataset$final_HIT_Assessment, 'A6' )

raw_greif_dataset$HIPA_DK <- dplyr::recode(raw_greif_dataset$final_HIT_Assessment, A1 = 0, A2 = 1, A3 = 1, A4 = 0, A5 = 0 )

class(raw_greif_dataset$HIPA_DK)

raw_greif_dataset$HIPA_DK <- as.factor(raw_greif_dataset$HIPA_DK)

class(raw_greif_dataset$HIPA_DK)

```

### Count OD above 0.5 and a control (HIPA_DK == 0)

```{r}
dplyr::count(raw_greif_dataset, HIPA_DK)
raw_greif_dataset %>% count(IgG > 0.5 & HIPA_DK == 0)

```

### Create gender variable: Count to make sure sex & gender variables are equal
```{r}
dplyr::count(raw_greif_dataset, sex)
raw_greif_dataset %>% group_by(sex) %>% summarise(n = n())

raw_greif_dataset$gender <- if_else(raw_greif_dataset$sex == 'm', 1,
                                                        if_else(raw_greif_dataset$sex == 'f',2, NA_real_))

dplyr::count(raw_greif_dataset, gender)
raw_greif_dataset$gender <- as.factor(raw_greif_dataset$gender)

```

### OD variable mutation
```{r}
class(raw_greif_dataset$IgG)
raw_greif_dataset$OD_pos <- if_else(raw_greif_dataset$IgG > 0.5, 1, if_else(raw_greif_dataset$IgG < 0.5, 0, NA_real_))

# Remove individuals with missing OD values 
precull <- count(raw_greif_dataset)
raw_greif_dataset <- filter(raw_greif_dataset, !is.na(IgG))
postcull <- count(raw_greif_dataset)
precull
postcull


```



### Create Tables - Table 1 & Table 2

```{r}
varss <- c("age", "gender", "IgG","IgA", 'IgM', "HIPA_DK", "OD_pos")
cat_varss <- c("gender", "HIPA_DK", "OD_pos")

tab1_greif <- CreateTableOne(vars = varss, data = raw_greif_dataset, factorVars = cat_varss)
tab1_greif


tab1_1_greif <- CreateTableOne(vars = varss, data = raw_greif_dataset, factorVars = cat_varss, strata = c('HIPA_DK'), testApprox = chisq.test, testNonNormal = T, includeNA = F)
tab1_1_greif

tab1_2 <- CreateTableOne(vars = varss, data = raw_greif_dataset, factorVars = cat_varss, strata = c('gender'), testApprox = chisq.test, testNonNormal = T)
tab1_2
```

## IgG quantification: Linear models for looking at assocations between IgG (outcome variable) against numerous predictor variables

### IgG and age
```{r}
#age
lin_igg <- lm (IgG ~ age, data = raw_greif_dataset)
summary(lin_igg)
#convert betas
exp(coef(lin_igg_gender_adj))


#age adjusted for gender
lin_igg_gender_adj <- lm (IgG ~ age + gender, data = raw_greif_dataset)
summary(lin_igg_gender_adj)

#convert betas
exp(coef(lin_igg_gender_adj))

# Check for homosketasticity of residuals

ggplot() + geom_point(aes(x = raw_greif_dataset$age, y = lin_igg$residuals))

# Normality

res <- lin_igg$residuals
res <- data.frame(res)

# GGplot of normality

ggplot(data = res, aes(res)) + geom_histogram(aes(y = ..density..), binwidth = .1, color = "blue") +
  stat_function(fun = dnorm, args = list(mean = mean(res$res), sd = sd(res$res)))

# Interaction between age and gender
lin_igg_age_gender <- lm (IgG ~ age*gender, data = raw_greif_dataset)
summary(lin_igg_age_gender)

interact_plot(lin_igg_age_gender, pred = age, modx = gender)

lin_igg_age_gender_subset <- lm (IgG ~ age*gender, data = raw_greif_dataset, subset = IgG > 0.5)
summary(lin_igg_age_gender_subset)

interact_plot(lin_igg_age_gender_subset, pred = age, modx = gender)


```


### Linear Regression on age and IgG, subset of HIPA_DK
```{r}

lin_hipa_igg <- lm(IgG ~ age, data = raw_greif_dataset, subset = HIPA_DK == 1)
summary(lin_hipa_igg)

ggplot(subset(raw_greif_dataset, HIPA_DK == 1 ), aes(x = age, y = IgG)) + geom_point() + geom_smooth(method = 'lm', formula = y ~ x, aes(col = 'lfit'))

lin_neghipa_igg <- lm(IgG ~ age, data = raw_greif_dataset, subset = HIPA_DK == 0)
summary(lin_neghipa_igg)

ggplot(subset(raw_greif_dataset, HIPA_DK == 0 ), aes(x = age, y = IgG)) + geom_point() + geom_smooth(method = 'lm', formula = y ~ x, aes(col = 'lfit'))
```


### IgG analysis with "positive" IgG patients

```{r}
# Linear regression on filter IgG

lin_igg_pos_subset <- lm (IgG ~ age, data = raw_greif_dataset, subset = IgG > 0.5)
summary(lin_igg_pos_subset)
exp(coef(lin_igg_pos_subset))
exp(confint(lin_igg_pos_subset))

ggplot(data = subset(raw_greif_dataset, IgG > 0.5), aes(x = age, y = IgG)) + geom_point() + geom_smooth(method = 'lm', formula = y ~ x, aes(col = 'lfit'))


```


### Linear regression on age and IgG, subset gender

```{r}
lin_age_igg_subsex <- lm(IgG ~ age, data = raw_greif_dataset, subset = gender == 1)

summary(lin_age_igg_subsex)

lin_age_igg_subsex_women <- lm(IgG ~ age, data = raw_greif_dataset, subset = gender == 2)

summary(lin_age_igg_subsex_women)

```



### IgG analysis with gender
```{r}
lin_igg_gender <- lm (IgG ~ gender, data = raw_greif_dataset)
summary(lin_igg_gender)

raw_grief_rmna_gender <- subset(raw_greif_dataset, !is.na(gender))

g <- ggplot(data =raw_grief_rmna_gender , aes(y = IgG, x = sex, fill = sex)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
geom_point(aes(y = IgG, color = sex), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
expand_limits(x = 2.25) +
guides(fill = FALSE) +
guides(color = FALSE) +
scale_color_brewer(palette = "Set1") +
scale_fill_brewer(palette = "Set1") +
coord_flip() +
theme_bw() +
raincloud_theme

g


# Lineary regression on gender and IgG, subset HIPA_DK

lin_sex_igg_hipasub <- lm(IgG ~ gender, data = raw_greif_dataset, subset = HIPA_DK == 1)
summary(lin_sex_igg_hipasub)


h <- ggplot(subset(raw_grief_rmsex, HIPA_DK == 1), aes(y = IgG, x = sex, fill = sex)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
geom_point(aes(y = IgG, color = sex), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
expand_limits(x = 2.25) +
guides(fill = FALSE) +
guides(color = FALSE) +
scale_color_brewer(palette = "Set1") +
scale_fill_brewer(palette = "Set1") +
coord_flip() +
theme_bw() +
raincloud_theme

h

# Linear regression on gender and IgG, subset HIPA negative patients

lin_sex_igg_hipaneg <- lm(IgG ~ gender, data = raw_greif_dataset, subset = HIPA_DK == 0)
summary(lin_sex_igg_hipaneg)

k <- ggplot(subset(raw_grief_rmsex, HIPA_DK == 0), aes(y = IgG, x = sex, fill = sex)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
geom_point(aes(y = IgG, color = sex), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
expand_limits(x = 2.25) +
guides(fill = FALSE) +
guides(color = FALSE) +
scale_color_brewer(palette = "Set1") +
scale_fill_brewer(palette = "Set1") +
coord_flip() +
theme_bw() +
raincloud_theme

k
```

### Linear regression with IgM 
```{r}
lin_age_igm <- lm(IgM ~ age, data = raw_greif_dataset)
summary(lin_age_igm)

# Plot the regression line
ggplot(data = raw_greif_dataset, aes(x = age, y = IgM)) + geom_point() + geom_smooth(method = 'lm', formula = y ~ x, aes(col = 'lfit'))

# Regression on age, subset HIPA positive individuals
lin_age_igm_hipasub <- lm(IgM ~ age, data = raw_greif_dataset, subset = HIPA_DK == 1)
summary(lin_age_igm_hipasub)

# Regression on age, subset HIPA negative individuals 
lin_age_igm_hipaneg <- lm(IgM ~ age, data = raw_greif_dataset, subset = HIPA_DK == 0)
summary(lin_age_igm_hipaneg)

# Regression on age, subset antibody (IgM) positive 
lin_age_igm_pos <- lm(IgM ~ age, data = raw_greif_dataset, subset = IgM > 0.5)
summary(lin_age_igm_pos)


# GENDER REGRESSION

lin_gender_igm <- lm(IgM ~ gender, data = raw_greif_dataset)
summary(lin_gender_igm)

# Regression on gender, subset HIPA positive individuals
lin_gender_igm_hipasub <- lm(IgM ~ gender, data = raw_greif_dataset, subset = HIPA_DK == 1)
summary(lin_gender_igm_hipasub)

# Regression on age, subset HIPA negative individuals 
lin_gender_igm_hipaneg <- lm(IgM ~ gender, data = raw_greif_dataset, subset = HIPA_DK == 0)
summary(lin_age_igm_hipaneg)

# Regression on age, subset antibody (IgM) positive 
lin_gender_igm_pos <- lm(IgM ~ gender, data = raw_greif_dataset, subset = IgA > 0.5)
summary(lin_age_igm_pos)

```



### Regression on IgA variable 
```{r}
lin_age_iga <- lm(IgA ~ age, data = raw_greif_dataset)
summary(lin_age_iga)

# Plot of association
ggplot(data = raw_greif_dataset, aes(x = age, y = IgA)) + geom_point() + geom_smooth(method = 'lm', formula = y ~ x, aes(col = 'lfit'))

# Regression on age, subset HIPA positive individuals
lin_age_iga_hipasub <- lm(IgA ~ age, data = raw_greif_dataset, subset = HIPA_DK == 1)
summary(lin_age_iga_hipasub)

# Regression on age, subset HIPA negative individuals 
lin_age_iga_hipaneg <- lm(IgA ~ age, data = raw_greif_dataset, subset = HIPA_DK == 0)
summary(lin_age_iga_hipaneg)

# Regression on age, subset antibody (IgM) positive 
lin_age_iga_pos <- lm(IgA ~ age, data = raw_greif_dataset, subset = IgA > 0.5)
summary(lin_age_iga_pos)


## GENDER association 


lin_gender_iga <- lm(IgA ~ gender, data = raw_greif_dataset)
summary(lin_gender_igm)

# Regression on gender, subset HIPA positive individuals
lin_gender_iga_hipasub <- lm(IgA ~ gender, data = raw_greif_dataset, subset = HIPA_DK == 1)
summary(lin_gender_iga_hipasub)

# Regression on age, subset HIPA negative individuals 
lin_gender_iga_hipaneg <- lm(IgA ~ gender, data = raw_greif_dataset, subset = HIPA_DK == 0)
summary(lin_gender_iga_hipaneg)

# Regression on age, subset antibody (IgA) positive 
lin_gender_iga_pos <- lm(IgA ~ gender, data = raw_greif_dataset, subset = IgA > 0.5)
summary(lin_gender_iga_pos)
```

### Correlation Analysis
```{r}

igg <- raw_greif_dataset$IgG
iga <- raw_greif_dataset$IgA
igm <- raw_greif_dataset$IgM

cor(igg,iga,use = 'complete.obs', method = c('spearman'))

cor(igg,igm,use = 'complete.obs', method = c('spearman'))

cor(iga,igm,use = 'complete.obs', method = c('spearman'))

cor_matrx <- matrix(c(raw_greif_dataset$IgG,raw_greif_dataset$IgA, raw_greif_dataset$IgM), ncol = 3, byrow = T)

crr <- cor(cor_matrx, use = 'complete.obs', method = c('spearman'))
corrplot(crr, method= 'number', is.corr = T)


cor_datafram<- data.frame(raw_greif_dataset$IgG,raw_greif_dataset$IgA, raw_greif_dataset$IgM)

crr <- cor(cor_datafram, use = 'complete.obs', method = c('spearman'))
corrplot(crr, method= 'number', is.corr = T)
```

## Logistic Regression on HIPA - Table 3

### GLM on age
```{r}

class(raw_greif_dataset$HIPA_DK)

lo_hipa_age_greif <- glm(as.factor(HIPA_DK) ~ age, data =  raw_greif_dataset, family = binomial(link =  'logit'))
summary(lo_hipa_age_greif)
exp(coef(lo_hipa_age_greif))
or_glm(raw_greif_dataset,lo_hipa_age_greif, incr = list(age = 1))

l <- ggplot(data = subset(raw_greif_dataset, !is.na(raw_greif_dataset$HIPA_DK)), aes(y = age, x = as.factor(HIPA_DK), fill = as.factor(HIPA_DK))) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
geom_point(aes(y = age, color = as.factor(HIPA_DK)), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
expand_limits(x = 2) +
guides(fill = FALSE) +
guides(color = FALSE) +
scale_color_brewer(palette = "Set1") +
scale_fill_brewer(palette = "Set1") +
coord_flip() +
theme_bw() +
raincloud_theme

l
```


### GLM on Gender
```{r}

lo_hipa_sex_greif <- glm(HIPA_DK ~ gender, data =  raw_greif_dataset, family = binomial(link =  'logit'))
summary(lo_hipa_sex_greif)
exp(coef(lo_hipa_sex_greif))

or_glm(raw_greif_dataset,lo_hipa_sex_greif)

ggplot(data = raw_greif_dataset, aes(x = HIPA_DK, fill = gender)) + geom_bar( position = 'fill')



```

### GLM on HIPA ~ age + sex
```{r}


# HIPA_DK variable 

lo_hipadk_sexage <- glm(HIPA_DK ~ gender +age, data =  raw_greif_dataset, family = binomial(link =  'logit'))
summary(lo_hipadk_sexage)

# reduced model
lo_hipadk_red <- glm(HIPA_DK ~ 1, data = raw_greif_dataset, family  = binomial(link = 'logit'))
summary(lo_hipadk_red)

# testing if model including gender and age is statistically 'better' than reduced model
lr.test(lo_hipadk_red, lo_hipadk_sexage)

or_glm(raw_greif_dataset, lo_hipadk_sexage, incr = list(log_age = 1, gender = 1))
```


### GLM on optical density 
```{r}
lo_hipa_igg_greif <- glm(HIPA_DK ~ IgG, data =  raw_greif_dataset, family = binomial(link =  'logit'))
summary(lo_hipa_igg_greif)
exp(coef(lo_hipa_igg_greif))

or_glm(raw_greif_dataset,lo_hipa_igg_greif, incr = list(IgG = 1))

g <- ggplot(data = raw_greif_dataset, aes(y = IgG, x = as.factor(HIPA_DK), fill = as.factor(HIPA_DK))) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
geom_point(aes(y = IgG, color = as.factor(HIPA_DK)), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
expand_limits(x = 2) +
guides(fill = FALSE) +
guides(color = FALSE) +
scale_color_brewer(palette = "Set1") +
scale_fill_brewer(palette = "Set1") +
coord_flip() +
theme_bw() +
raincloud_theme

g

ggsave(plot = last_plot(), filename = 'sra_od_greif.png', height = 5, width = 5)
```


## GLM on IgM

```{r}
reg_sra_igM__greif <- glm(HIPA_DK ~ IgM, data =  raw_greif_dataset, family = binomial(link =  'logit'))

summary(reg_sra_igM__greif)
exp(coef(reg_sra_igM__greif))
or_glm(raw_greif_dataset, reg_sra_igM__greif, incr = list(IgM = 1))
```

## GLM on Iga

```{r}
reg_sra_igA__greif <- glm(HIPA_DK ~ IgA, data =  raw_greif_dataset, family = binomial(link =  'logit'))

summary(reg_sra_igA__greif)
exp(coef(reg_sra_igA__greif))
or_glm(raw_greif_dataset, reg_sra_igA__greif, incr = list(IgA = 1))
```


## Stepwise backwards regression modeling, Youden's J - Table 4

```{r}
# Creating data frame with just Variable that are to be including in backwards regression and removing NAs as they are problematic in prediction models 

greif_demographic_naomit <- filter(raw_greif_dataset, !is.na(IgG) & !is.na(age) & !is.na(gender) & !is.na(HIPA_DK))

# Creating model
fit1_greif <- glm(data = greif_demographic_naomit, HIPA_DK ~ IgG + gender + age, family = binomial(link = 'logit') )

#Selecting of variables 
step_model_greif <- fit1_greif %>% stepAIC(trace = T)
# Summary stats of model
summary(step_model_greif)
exp(coef(step_model_greif))
exp(confint(step_model_greif))
# Variance inflation factor aka collinearity 
car::vif(step_model_greif)


# Youden's for HIPA prediction using backwards regression variables (retained)

raw_greif_dataset_backwards_df <- filter(raw_greif_dataset, !is.na(IgG) & !is.na(HIPA_DK) & !is.na(gender)) 

fit2_greif <- glm(data = raw_greif_dataset_backwards_df, HIPA_DK ~ IgG + gender, family = binomial(link = 'logit'))

forward_step_preds_greif <- predict(fit2_greif)

raw_greif_dataset_backwards_df$predictor_stepwise <- forward_step_preds_greif
raw_greif_dataset_backwards_df$outcome_stepwise <- raw_greif_dataset_backwards_df$HIPA_DK

cut_youdens_stepwise_greif <- cutpointr(raw_greif_dataset_backwards_df, predictor_stepwise, outcome_stepwise, method = maximize_metric, metric = youden, na.rm = T)

summary(cut_youdens_stepwise_greif)


# Youden's for HIPA prediction with just IgG variable

fit3_greif <- glm(data = raw_greif_dataset_backwards_df, HIPA_DK ~ IgG, family = binomial(link = 'logit'))

forward_step_igg_greif <- predict(fit3_greif)

raw_greif_dataset_backwards_df$predictor_igg_stepwise <- forward_step_igg_greif
raw_greif_dataset_backwards_df$outcome_stepwise <- raw_greif_dataset_backwards_df$HIPA_DK

cut_youdens_igg_greifwald <- cutpointr(raw_greif_dataset_backwards_df, predictor_igg_stepwise, outcome_stepwise, method = maximize_metric, metric = youden, na.rm = T)

summary(cut_youdens_igg_greifwald)


# COMPARING IF THE FULL MODEL DOES BETTER AT PREDICTION VS. JUST ANTIBODY ALONE

reg_sra_igg_grief <- glm(HIPA_DK ~ IgG, data = raw_greif_dataset_backwards_df, family = binomial(link = 'logit'))
stepwise_reg_model_greif <- glm(data = raw_greif_dataset_backwards_df, HIPA_DK ~ IgG + gender, family = binomial(link = 'logit'))

lr.test(stepwise_reg_model_greif, reg_sra_igg_grief)

lmtest::lrtest(stepwise_reg_model_greif, reg_sra_igg_grief)

AIC(stepwise_reg_model_greif,reg_sra_igg_grief)
```



## Youdens J and ROC for best dichotimizing for IgG and HIPA - Table 5

```{r}
# creating subset dataframe for only necessary variables
optimal_cut_youdens_greif_df <- raw_greif_dataset %>% dplyr::select(IgG, HIPA_DK, gender)

greif_optimal_cut_df <- optimal_cut_youdens_greif_df %>% dplyr::select(predictor = IgG, outcome = HIPA_DK) %>% mutate(cohort = 'Greif')

class(greif_optimal_cut_df)

greif_optimal_cut_df <- as.data.frame(greif_optimal_cut_df)

class(greif_optimal_cut_df)

# Running cutpointr to find optimal cutpoint 
cut_youdens_grief <- cutpointr(greif_optimal_cut_df, predictor, outcome, method = maximize_metric, metric = youden, na.rm = T)

summary(cut_youdens_grief)
plg <- plot_metric(cut_youdens_grief)

plg + ggtitle('Grief - Antibody Cutpoint for HIT Determination') + theme_minimal()

# Manual Cutpoints

optimal_cut_youdens_greif_df$predictor <- optimal_cut_youdens_greif_df$IgG
optimal_cut_youdens_greif_df$outcome <- optimal_cut_youdens_greif_df$HIPA_DK

cut_youdens_manual_0.4 <- cutpointr(greif_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 0.4, na.rm = T)

summary(cut_youdens_manual_0.4)


cut_youdens_manual_1.0 <- cutpointr(greif_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 1.0, na.rm = T)

summary(cut_youdens_manual_1.0)

cut_youdens_manual_1.5 <- cutpointr(greif_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 1.5, na.rm = T)

summary(cut_youdens_manual_1.5)

cut_youdens_manual_2.0 <- cutpointr(greif_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 2.0, na.rm = T)

summary(cut_youdens_manual_2.0)

cut_youdens_manual_2.5 <- cutpointr(greif_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 2.5, na.rm = T)

summary(cut_youdens_manual_2.5)

cut_youdens_manual_3.0 <- cutpointr(greif_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 3.0, na.rm = T)

summary(cut_youdens_manual_3.0)

```



## Including OD, age and gender (common variables in all 3 cohorts)

```{r}
reg_sra_od_age_gender_greif <- glm(HIPA_DK ~ gender + age + IgG, data =  raw_greif_dataset, family = binomial(link =  'logit'))

summary(reg_sra_od_age_gender_greif)
exp(coef(reg_sra_od_age_gender_greif))
or_glm(raw_greif_dataset, reg_sra_od_age_gender_greif, incr = list(IgG = 1, age = 1))
```