---
title: "McMaster Demographic Analysis"
author: "Jason Giles"
date: "2023-06-29"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Installing packages and reading in data
```{r}
library(pscl)
library(tidyverse)
library(MESS)
library(haven)
library(here)
library(psych)
library(skimr)
library(DataExplorer)
library(visdat)
library(mdscore)
library(oddsratio)
library(ppcor)
library(corrplot)
library(corrr)
library(readr)
library(tidyr)
library(ggplot2)
library(Hmisc)
library(RColorBrewer)
library(reshape2)
library(PupillometryR)
library(corrplot)
library(corrr)
library(MASS)
library(bestNormalize)
library(readxl)
library(car)
library(tableone)
library(olsrr)
library(MASS)
library(cutpointr)
library(car)
library(OptimalCutpoints)
library(lmtest)
library(pROC)
library(pastecs)
library(dplyr)
library(readr)
library(here)


here()

raw_mcmaster_dataset <- read_csv(here("../all_HIT_Nov29.csv"))

# Renaming variables to removed quotes

raw_mcmaster_dataset <- dplyr::rename(raw_mcmaster_dataset, new_abo = "new ABO IDs", sample_year = 'Sample Year', age = 'AGE at HIT-trunc', 
                       call_for_abo = 'CALL FOR ABO', SRA = 'SRA call', IgG = 'EIA-G', IgP = "GTI-GAM")
```


### Exploring & Cleaning of the data 

```{r}
summary(raw_mcmaster_dataset)
skim(raw_mcmaster_dataset)

# Creating data so variables are factor levels instead of numeric 
raw_mcmaster_dataset$SEX[raw_mcmaster_dataset$SEX == 'M'] <- 1
raw_mcmaster_dataset$SEX[raw_mcmaster_dataset$SEX == 'F'] <- 2

class(raw_mcmaster_dataset$SEX)
raw_mcmaster_dataset$SEX <- as.factor(raw_mcmaster_dataset$SEX)
class(raw_mcmaster_dataset$SEX)

# Re-coding functional assay 
raw_mcmaster_dataset$SRA[raw_mcmaster_dataset$SRA == 'SRA POS'] <- 1
raw_mcmaster_dataset$SRA[raw_mcmaster_dataset$SRA == 'SRA NEG'] <- 0
raw_mcmaster_dataset$SRA[raw_mcmaster_dataset$SRA == "SRA ND"] <- NA_integer_

raw_mcmaster_dataset %>% group_by(SRA) %>% count

raw_mcmaster_dataset$SRA <- as.factor(raw_mcmaster_dataset$SRA)

# Re-coding surgery variable
raw_mcmaster_dataset$Surgery_Patient[raw_mcmaster_dataset$Surgery_Patient == 'Yes'] <- 1
raw_mcmaster_dataset$Surgery_Patient[raw_mcmaster_dataset$Surgery_Patient == 'No'] <- 0

raw_mcmaster_dataset$Surgery_Patient[raw_mcmaster_dataset$Surgery_Patient == 'unknown'] <- NA

raw_mcmaster_dataset$Surgery_Patient <- as.factor(raw_mcmaster_dataset$Surgery_Patient)

#Creating blood type O/non-O group
raw_mcmaster_dataset$O_type <- if_else(raw_mcmaster_dataset$GROUP == 'O', 1, 0)
raw_mcmaster_dataset$O_type <- as.factor(raw_mcmaster_dataset$O_type)

# Creating OD variable
raw_mcmaster_dataset$OD <- if_else(!is.na(raw_mcmaster_dataset$IgG), raw_mcmaster_dataset$IgG, raw_mcmaster_dataset$IgP)
dplyr::count(raw_mcmaster_dataset, is.na(IgG))
dplyr::count(raw_mcmaster_dataset, is.na(IgP))
dplyr::count(raw_mcmaster_dataset, is.na(OD))

dplyr::count(raw_mcmaster_dataset, !is.na(IgG) & !is.na(IgP))


# add categorical variable for OD positvitiy
raw_mcmaster_dataset$OD_pos <- if_else(raw_mcmaster_dataset$OD > 0.5, 1, if_else(raw_mcmaster_dataset$OD < 0.5, 0, NA_real_))


#Remove all individuals with missing OD values

raw_mcmaster_dataset <- filter(raw_mcmaster_dataset, !is.na(OD))


dplyr::count(raw_mcmaster_dataset, is.na(Surgery_Patient))
```


### Rainbow plotting

```{r}
raincloud_theme = theme(
text = element_text(size = 10),
axis.title.x = element_text(size = 16),
axis.title.y = element_text(size = 16),
axis.text = element_text(size = 14),
axis.text.x = element_text(angle = 45, vjust = 0.5),
legend.title=element_text(size=16),
legend.text=element_text(size=16),
legend.position = "right",
plot.title = element_text(lineheight=.8, face="bold", size = 16),
panel.border = element_blank(),
panel.grid.minor = element_blank(),
panel.grid.major = element_blank(),
axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))

# Summary statsitics for the plots

lb <- function(x) mean(x) - sd(x)
ub <- function(x) mean(x) + sd(x)


```

## COUNTING NAs \ Basic plotting

```{r}
count(raw_mcmaster_dataset,is.na(raw_mcmaster_dataset$age))

ggplot(data = raw_mcmaster_dataset, aes(age)) + geom_histogram(aes(y = ..density..), binwidth = 2, color = "blue") + stat_function(fun = dnorm, args = list(mean = mean(raw_mcmaster_dataset$age), sd = sd(raw_mcmaster_dataset$age)))

ggsave(plot = last_plot(), filename = 'age_distribution_mcmaster.png', height = 5, width = 5)


# count of total non-missing IgG


sum(is.na(raw_mcmaster_dataset$IgG))
summary(raw_mcmaster_dataset$IgG)

sum(is.na(raw_mcmaster_dataset$IgP))
summary(raw_mcmaster_dataset$IgP)

sum(is.na(raw_mcmaster_dataset$OD))
summary(raw_mcmaster_dataset$OD)

summary(raw_mcmaster_dataset$SRA)
filter(raw_mcmaster_dataset, OD < 0.4) %>% count((SRA))


```


## Creating Table 1, Table 2

```{r}
dplyr::count(raw_mcmaster_dataset, raw_mcmaster_dataset$Surgery_Patient == 1)
dplyr::count(raw_mcmaster_dataset, Surgery_Patient)
sum(is.na(raw_mcmaster_dataset$Surgery_Patient))

varss_mcmaster <- c("age", "SEX", "OD","SRA", "GROUP", "RH","Surgery_Patient", "O_type", "OD_pos")
cat_varss_mcmaster <- c("SEX", "SRA", "GROUP","RH", "Surgery_Patient", 'O_type', 'OD_pos')

#Table 1 generation
tab1_mcmaster <- CreateTableOne(vars = varss_mcmaster, data = raw_mcmaster_dataset, factorVars = cat_varss_mcmaster, includeNA = T)
tab1_mcmaster

# Table 2, stratification
tab2_mcmaster <-  CreateTableOne(vars = varss_mcmaster, data = raw_mcmaster_dataset, factorVars = cat_varss_mcmaster, strata = 'SRA', testApprox = chisq.test, testNonNormal = T, includeNA = F)
tab2_mcmaster


# Summary statistics on only O blood group
tab1_11 <- CreateTableOne(vars = varss, data = subset(raw_mcmaster_dataset, raw_mcmaster_dataset$GROUP == 'O'), factorVars = cat_varss, testApprox = chisq.test, testNonNormal = T)
tab1_11

# Summary stats grouped by gender
tab1_2 <- CreateTableOne(vars = varss, data = raw_mcmaster_dataset, factorVars = cat_varss, strata = 'SEX', testNonNormal = T)
tab1_2

# GROUP by surgery
tab1_3 <- CreateTableOne(vars = varss, data = raw_mcmaster_dataset, factorVars = cat_varss, strata = c('Surgery_Patient'), testApprox = chisq.test, testNonNormal = T)
tab1_3

# Group by Rhesus antigen
tab1_4 <- CreateTableOne(vars = varss, data = raw_mcmaster_dataset, factorVars = cat_varss, strata = c('RH'), testApprox = chisq.test, testNonNormal = T)
tab1_4

# Group by blood type
tab1_5 <- CreateTableOne(vars = varss_mcmaster, data = raw_mcmaster_dataset, factorVars = cat_varss_mcmaster, strata = c('GROUP'), testApprox = chisq.test, testNonNormal = T, includeNA = T)
tab1_5

# Stratify by O/non-O 
tab1_6 <- CreateTableOne(vars = varss_mcmaster, data = raw_mcmaster_dataset, factorVars = cat_varss_mcmaster, strata = c('O_type'), testApprox = chisq.test, testNonNormal = T)
tab1_6

```


### Logistic regression on Functional Assay (SRA) and IgG
```{r}

reg_sra_igg_mcmaster <- glm(SRA ~ OD, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))
summary(reg_sra_igg_mcmaster)
exp(coef(reg_sra_igg_mcmaster))
or_glm(raw_mcmaster_dataset,reg_sra_igg_mcmaster, incr = list(OD = 1))

# Association of OD, adjustment for age
reg_sra_igg_age_mcmaster <- glm(SRA ~ OD + age, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))
summary(reg_sra_igg_age_mcmaster)
exp(coef(reg_sra_igg_age_mcmaster))
or_glm(raw_mcmaster_dataset,reg_sra_igg_age_mcmaster, incr = list(OD = 1, age = 1))

# Association of OD, adjustment for age and sex

reg_sra_igg_age_sex_mcmaster <- glm(SRA ~ OD + age + SEX, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))
summary(reg_sra_igg_age_sex_mcmaster)
exp(coef(reg_sra_igg_age_sex_mcmaster))

or_glm(raw_mcmaster_dataset,reg_sra_igg_age_sex, incr = list(OD = 1, age = 1))



```


### Logistic regression on Functional Assay (SRA) and AGE
```{r}

reg_sra_age_mcmaster <- glm(SRA ~ age, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))

summary(reg_sra_age_mcmaster)
exp(coef(reg_sra_age_mcmaster))
or_glm(raw_mcmaster_dataset,reg_sra_age_mcmaster, incr = list(age = 1))

# Plot of association of age
g <- ggplot(data = subset(raw_mcmaster_dataset, !is.na(raw_mcmaster_dataset$SRA)), aes(y = age, x = SRA, fill = SRA)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) + 
geom_point(aes(y = age, color = SRA), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
expand_limits(x = 2) +
guides(fill = FALSE) +
guides(color = FALSE) +
scale_color_brewer(palette = "Set1") +
scale_fill_brewer(palette = "Set1") +
coord_flip() +
theme_bw() +
raincloud_theme

g

ggsave(plot = last_plot(), filename = 'sra_age_mcmaster.png', height = 5, width = 5)

# Association of age on SRA stratified by gender
reg_sra_age_subsex_mcmaster <- glm(SRA ~ age, data = subset(raw_mcmaster_dataset, SEX ==2), family = binomial(link = 'logit'))

summary(reg_sra_age_subsex_mcmaster)
exp(coef(reg_sra_age_subsex_mcmaster))

```


### Logistic regression on Functional Assay (SRA) and Sex   
```{r}
reg_sra_gender_mcmaster <- glm(SRA ~ SEX, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))

class(raw_mcmaster_dataset$SEX)

summary(reg_sra_gender_mcmaster)
exp(coef(reg_sra_gender_mcmaster))

or_glm(raw_mcmaster_dataset,reg_sra_gender_mcmaster)

#adjusted for age
reg_sra_gender_age_mcmaster <- glm(SRA ~ SEX + age, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))

summary(reg_sra_gender_age_mcmaster)
exp(coef(reg_sra_gender_age_mcmaster))


# Is there confounding of blood type

reg_sra_gender_otype <- glm(SRA ~ SEX+O_type, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))
summary(reg_sra_gender_otype)
exp(coef(reg_sra_gender_otype))


## Is there confounding of blood type

reg_sra_gender_otype <- glm(SRA ~ SEX+GROUP, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))
summary(reg_sra_gender_otype)
exp(coef(reg_sra_gender_otype))


# confounding between SEX and RH 

reg_sra_gender_rh <- glm(SRA ~ SEX+RH+O_type, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))
summary(reg_sra_gender_rh)
exp(coef(reg_sra_gender_rh))

```


### Logistic regression on Functional Assay (SRA) and Rhesus antigen    
```{r}
reg_sra_RH_mcmaster <- glm(SRA ~ RH, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))

summary(reg_sra_RH_mcmaster)
exp(coef(reg_sra_RH_mcmaster))

or_glm(raw_mcmaster_dataset, reg_sra_RH_mcmaster)

# Adjustment for gender
reg_sra_RH_gender_mcmaster <- glm(SRA ~ RH + SEX, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))

summary(reg_sra_RH_gender_mcmaster)
exp(coef(reg_sra_RH_gender_mcmaster))

# adjustment for type O blood
reg_sra_RH_otype <- glm(SRA ~ RH + O_type, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))

summary(reg_sra_RH_otype)
exp(coef(reg_sra_RH_otype))

# Adjustment for surgery
reg_sra_RH_surgery <- glm(SRA ~ RH + Surgery_Patient, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))

summary(reg_sra_RH_surgery)
exp(coef(reg_sra_RH_surgery))
```


### Logistic regression on Functional Assay (SRA) and Blood group   
```{r}
reg_sra_abo_mcmaster <- glm(SRA ~ GROUP, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))

summary(reg_sra_abo_mcmaster)
exp(coef(reg_sra_abo_mcmaster))

or_glm(raw_mcmaster_dataset,reg_sra_abo_mcmaster)

raw_mcmaster_dataset %>% 
  filter(!is.na(SRA),!is.na(GROUP)) %>% 
  ggplot() + 
  geom_bar(aes( x = SRA, fill = as.factor(GROUP)), position = 'fill') + theme_minimal()

# effect of Rhesus on ABO 
reg_sra_abo_RH_mcmaster <- glm(SRA ~ GROUP + RH, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))

summary(reg_sra_abo_RH_mcmaster)
exp(coef(reg_sra_abo_RH_mcmaster))

# Is there an effect between blood type and surgery
reg_sra_group_surgery <- glm(SRA ~ GROUP + Surgery_Patient, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))

summary(reg_sra_group_surgery)
exp(coef(reg_sra_group_surgery))


## ABO blood group adjusted for Sex and age

reg_sra_abo_full <- glm(SRA ~ GROUP + SEX + age, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))

summary(reg_sra_abo_full)
exp(coef(reg_sra_abo_full))

or_glm(raw_mcmaster_dataset,reg_sra_abo_full, incr = list(age = 1))


h <- ggplot(data = subset(raw_mcmaster_dataset, !is.na(raw_mcmaster_dataset$GROUP)), aes(y = OD, x = GROUP, fill = GROUP)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) + 
geom_point(aes(y = OD, color = GROUP), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
expand_limits(x = 2) +
guides(fill = FALSE) +
guides(color = FALSE) +
scale_color_brewer(palette = "Set1") +
scale_fill_brewer(palette = "Set1") +
coord_flip() +
theme_bw() +
raincloud_theme

h


p <- ggplot(data = subset(raw_mcmaster_dataset, !is.na(raw_mcmaster_dataset$GROUP) & raw_mcmaster_dataset$OD > 0), aes(x = GROUP, y = OD, fill = GROUP)) + geom_violin(trim=T) +
   geom_boxplot(width=0.1, outlier.shape = NA ) + theme_minimal()
p

p + scale_fill_brewer(palette="GnBu")

ggsave(plot = last_plot(), filename = 'abo_OD_violin_mcmaster.png', height = 5, width = 5)
p + scale_fill_grey() + theme_classic()
p + geom_jitter(shape=16, position=position_jitter(0.2))

```

## Regression on SRA and non-O


```{r}
reg_sra_nono <- glm(SRA ~ O_type, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))

summary(reg_sra_nono)
exp(coef(reg_sra_nono))

or_glm(raw_mcmaster_dataset,reg_sra_nono)

raw_mcmaster_dataset %>% 
  filter(!is.na(SRA),!is.na(O_type)) %>% 
  ggplot() + 
  geom_bar(aes( x = SRA, fill = as.factor(O_type)), position = 'fill') + theme_minimal()

## Effect of age and gender

reg_sra_abo_full_mcmaster <- glm(SRA ~ O_type + SEX + age, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))

summary(reg_sra_abo_full_mcmaster)
exp(coef(reg_sra_abo_full_mcmaster))
or_glm(raw_mcmaster_dataset,reg_sra_abo_full_mcmaster, incr = list(age = 1))


# Is there an effect between O type and surgery
reg_sra_group_surgery <- glm(SRA ~ O_type + Surgery_Patient, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))

summary(reg_sra_group_surgery)
exp(coef(reg_sra_group_surgery))



```


### Logistic regression on Functional Assay (SRA) and Surgery
```{r}
reg_sra_surgery_mcmaster <- glm(SRA ~ Surgery_Patient, data = subset(raw_mcmaster_dataset, !is.na(Surgery_Patient)), family = binomial(link = 'logit'))

summary(reg_sra_surgery_mcmaster)
exp(coef(reg_sra_surgery_mcmaster))
or_glm(raw_mcmaster_dataset,reg_sra_surgery_mcmaster)

# Effect of age on surgery
reg_rs_surgery_age <- glm(SRA ~ Surgery_Patient + age, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))

summary(reg_rs_surgery_age)
exp(coef(reg_rs_surgery_age))

# Effect of gender on surgery

# Is there an interaction between Surgery and SEX

reg_rs_surgery_sex <- glm(SRA ~ Surgery_Patient + SEX, data = raw_mcmaster_dataset, family = binomial(link = 'logit'))

summary(reg_rs_surgery_sex)
exp(coef(reg_rs_surgery_sex))
```

## Stepwise backwards regression modeling, Youden's J - Table 4

```{r}

class(raw_mcmaster_dataset$Surgery_Patient)
class(raw_mcmaster_dataset$GROUP)

fit1_mcmaster <- glm(data = raw_mcmaster_dataset , SRA ~ age + SEX + OD + Surgery_Patient + as.factor(GROUP) + RH, family = binomial(link = 'logit'))
summary(fit1_mcmaster)

count(raw_mcmaster_dataset, Surgery_Patient)

# FIT remvoing NAs
raw_mcmaster_nosurg <- filter(raw_mcmaster_dataset, !is.na(OD) & !is.na(SRA) & !is.na(SEX) & !is.na(GROUP) & !is.na(RH) & !is.na(Surgery_Patient))

raw_mcmaster_nosurg_dropsurg <- subset(raw_mcmaster_nosurg, select = -Surgery_Patient)

fit1_mcmaster <- glm(data = raw_mcmaster_nosurg, SRA ~  age + SEX + OD + as.factor(GROUP) + RH , family = binomial(link = 'logit'))

#sum(is.na(raw_mcmaster$Surgery_Patient))

#---------------------------------------------------------------------------------------------
step_model <- fit1_mcmaster %>% stepAIC(trace = T)

summary(step_model)

exp(coef(step_model))

exp(confint(step_model))

or_glm(raw_mcmaster_dataset, step_model, incr = list(OD = 1, age = 1))

# Youdens calculation
raw_mcmaster_dataset_backwards_df <- filter(raw_mcmaster_dataset, !is.na(OD) & !is.na(SEX) & !is.na(SRA))

fit2_mcmaster <- glm(data = raw_mcmaster_dataset_backwards_df, SRA ~ SEX + OD , family = binomial(link = 'logit'))


forward_step_preds_tours <- predict(fit2_mcmaster)

raw_mcmaster_dataset_backwards_df$predictor_stepwise <- forward_step_preds_tours
raw_mcmaster_dataset_backwards_df$outcome_stepwise <- raw_mcmaster_dataset_backwards_df$SRA

cut_youdens_stepwise_mcmaster <- cutpointr(raw_mcmaster_dataset_backwards_df, predictor_stepwise, outcome_stepwise, method = maximize_metric, metric = youden, na.rm = T)

summary(cut_youdens_stepwise_mcmaster)

# cOMPARING IF THE FULL MODEL DOES BETTER AT PREDICTION VS. JUST ANTIBODY ALONE



reg_sra_igg_mcmaster <- glm(SRA ~ OD, data = raw_mcmaster_dataset_backwards_df, family = binomial(link = 'logit'))
stepwise_reg_model <- glm(data = raw_mcmaster_dataset_backwards_df , SRA ~ SEX + OD, family = binomial(link = 'logit'))


lr.test(reg_sra_igg_mcmaster, stepwise_reg_model)

lmtest::lrtest(stepwise_reg_model, reg_sra_igg_mcmaster)

AIC(stepwise_reg_model,reg_sra_igg_mcmaster)


```



### Sensitivity Analysis of Ig Polyclonal vs IgG 
```{r}
# Using IgP vs IgG for regression model
raw_mcmaster_na_ipg_igg_only <- dplyr::filter(raw_mcmaster_dataset, !is.na(SRA) & !is.na(SEX) & !is.na(IgP) & !is.na(IgG)) 

fitigp_mcmaster <- glm(data = raw_mcmaster_na_ipg_igg_only, SRA ~ IgP + SEX, family = binomial(link = 'logit'))
forward_step_preds_mcmaster <- predict(fitigp_mcmaster)

raw_mcmaster_na_ipg_igg_only$predictor_stepwise <- forward_step_preds_mcmaster
raw_mcmaster_na_ipg_igg_only$outcome_stepwise <- raw_mcmaster_na_ipg_igg_only$SRA

cut_youdens_stepwise_igp <- cutpointr(raw_mcmaster_na_ipg_igg_only, predictor_stepwise, outcome_stepwise, method = maximize_metric, metric = youden, na.rm = T)

summary(cut_youdens_stepwise_igp)

pROC::auc(raw_mcmaster_na_ipg_igg_only$SRA, raw_mcmaster_na_ipg_igg_only$predictor_stepwise)

# NOW IgG

fitigg_mcmaster <- glm(data = raw_mcmaster_na_ipg_igg_only, SRA ~ IgG + SEX, family = binomial(link = 'logit'))
forward_step_preds_mcmaster <- predict(fitigg_mcmaster)

raw_mcmaster_na_ipg_igg_only$predictor_stepwise <- forward_step_preds_mcmaster
raw_mcmaster_na_ipg_igg_only$outcome_stepwise <- raw_mcmaster_na_ipg_igg_only$SRA

cut_youdens_stepwise_igg <- cutpointr(raw_mcmaster_na_ipg_igg_only, predictor_stepwise, outcome_stepwise, method = maximize_metric, metric = youden, na.rm = T)

summary(cut_youdens_stepwise_igg)

pROC::auc(raw_mcmaster_na_ipg_igg_only$SRA, raw_mcmaster_na_ipg_igg_only$predictor_stepwise)

lrtest(fitigp_mcmaster, fitigg_mcmaster)
```




## Youdens J and ROC for best dichotimizing for IgG and HIPA - Table 5

```{r}
# creating subset dataframe for only necessary variables
optimal_cut_youdens_mcmaster_df <- raw_mcmaster_dataset %>% dplyr::select(OD, SRA, SEX)

mcmaster_optimal_cut_df <- optimal_cut_youdens_mcmaster_df %>% dplyr::select(predictor = OD, outcome = SRA) %>% mutate(cohort = 'mcmaster')

class(mcmaster_optimal_cut_df)

mcmaster_optimal_cut_df <- as.data.frame(mcmaster_optimal_cut_df)

class(mcmaster_optimal_cut_df)

# Running cutpointr to find optimal cutpoint 
cut_youdens_tours <- cutpointr(mcmaster_optimal_cut_df, predictor, outcome, method = maximize_metric, metric = youden, na.rm = T)

summary(cut_youdens_tours)
plg <- plot_metric(cut_youdens_tours)

plg + ggtitle('McMaster - Antibody Cutpoint for HIT Determination') + theme_minimal()

# Manual Cutpoints

cut_youdens_manual_0.4 <- cutpointr(mcmaster_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 0.4, na.rm = T)

summary(cut_youdens_manual_0.4)


cut_youdens_manual_1.0 <- cutpointr(mcmaster_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 1.0, na.rm = T)

summary(cut_youdens_manual_1.0)

cut_youdens_manual_1.5 <- cutpointr(mcmaster_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 1.5, na.rm = T)

summary(cut_youdens_manual_1.5)

cut_youdens_manual_2.0 <- cutpointr(mcmaster_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 2.0, na.rm = T)

summary(cut_youdens_manual_2.0)

cut_youdens_manual_2.5 <- cutpointr(mcmaster_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 2.5, na.rm = T)

summary(cut_youdens_manual_2.5)

cut_youdens_manual_3.0 <- cutpointr(mcmaster_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 3.0, na.rm = T)

summary(cut_youdens_manual_3.0)

```



## Including OD, age and gender (common variables in all 3 cohorts)

```{r}
reg_sra_od_age_gender_mcmaster <- glm(SRA ~ OD + age + SEX, data = raw_mcmaster, family = binomial(link = 'logit'))

summary(reg_sra_od_age_gender_mcmaster)
exp(coef(reg_sra_od_age_gender_mcmaster))
or_glm(raw_mcmaster, reg_sra_od_age_gender_mcmaster, incr = list(OD = 1, age = 1))

reg_sra_od_age_gender_mcmaster <- glm(SRA ~ OD + age + SEX, data = subset(raw_mcmaster, OD > 0.5), family = binomial(link = 'logit'))
```