---
title: "Tours Demographic Analysis"
author: "Jason Giles"
date: "2023-06-27"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Installing packages and reading in data
```{r}
library(pscl)
library(tidyverse)
library(MESS)
library(haven)
library(here)
library(psych)
library(skimr)
library(DataExplorer)
library(visdat)
library(mdscore)
library(oddsratio)
library(ppcor)
library(corrplot)
library(corrr)
library(readr)
library(tidyr)
library(ggplot2)
library(Hmisc)
library(RColorBrewer)
library(reshape2)
library(PupillometryR)
library(corrplot)
library(corrr)
library(MASS)
library(bestNormalize)
library(readxl)
library(car)
library(tableone)
library(olsrr)
library(MASS)
library(cutpointr)
library(car)
library(OptimalCutpoints)
library(lmtest)
library(pROC)
library(pastecs)
library(dplyr)
library(readr)
library(here)

getwd()
here()
# read in Tours file
raw_tours_dataset <- read_delim((here("../TOURS_covariate.txt")), delim = "\t")
```

### Exploration of the data & summary - Cleaning of data
```{r}
skim(raw_tours_dataset)
summary(raw_tours_dataset)

#Replace -9 value with NA
raw_tours_dataset[raw_tours_dataset == -9] <- NA
summary(raw_tours_dataset)

# Filter for anyone 18 or older

raw_tours_dataset <- raw_tours_dataset %>% dplyr::filter(is.na(age) | age >= 18)

# Filter anyone missing OD values 

raw_tours_dataset <- filter(raw_tours_dataset, !is.na(OD))

# visualizing the overall data structure
vis_miss(raw_tours_dataset)
vis_dat(raw_tours_dataset)
# Count if any repeats of IID

n_occur <- data.frame(table(raw_tours_dataset$IID))

n_occur[n_occur$Freq >1, ]

### Cleaning of the data
raw_tours_dataset$gender <- as.factor(raw_tours_dataset$gender)
raw_tours_dataset$CPBnew <- as.factor(raw_tours_dataset$CPBnew)
raw_tours_dataset$SRAnew <- as.factor(raw_tours_dataset$SRAnew)
raw_tours_dataset$SRAnew2 <- as.factor(raw_tours_dataset$SRAnew2)
raw_tours_dataset$HIT_trend <- as.factor(raw_tours_dataset$HIT_trend)
raw_tours_dataset$thrombosisnew <- as.factor(raw_tours_dataset$thrombosisnew)
raw_tours_dataset$UFH <- as.factor(raw_tours_dataset$UFH)

# Creating OD_pos variable
raw_tours_dataset$OD_pos <- if_else(raw_tours_dataset$OD > 0.5, 1, if_else(raw_tours_dataset$OD < 0.5, 0, NA_real_))


class(raw_tours_dataset$age)

# Visualization of age

ggplot(data = raw_tours_dataset, aes(age)) + geom_histogram(aes(y = ..density..), binwidth = 2, color = "blue") + stat_function(fun = dnorm, args = list(mean = mean(raw_tours_dataset$age), sd = sd(raw_tours_dataset$age)))


```

### Rainbow plotting

```{r}
raincloud_theme = theme(
text = element_text(size = 10),
axis.title.x = element_text(size = 16),
axis.title.y = element_text(size = 16),
axis.text = element_text(size = 14),
axis.text.x = element_text(angle = 45, vjust = 0.5),
legend.title=element_text(size=16),
legend.text=element_text(size=16),
legend.position = "right",
plot.title = element_text(lineheight=.8, face="bold", size = 16),
panel.border = element_blank(),
panel.grid.minor = element_blank(),
panel.grid.major = element_blank(),
axis.line.x = element_line(colour = 'black', size=0.5, linetype='solid'),
axis.line.y = element_line(colour = 'black', size=0.5, linetype='solid'))

# Summary statsitics for the plots

lb <- function(x) mean(x) - sd(x)
ub <- function(x) mean(x) + sd(x)


```

### Create Tables - Table 1 & Table 2
```{r}
?CreateTableOne
varss <- c("age", "gender", "OD","SRAnew2", "UFH", "PLT_before","CPBnew", 'OD_pos')
cat_varss <- c("gender", "SRAnew2", "UFH","CPBnew", 'OD_pos')

# Creating Table 1
tab1 <- CreateTableOne(vars = varss, data = raw_tours_dataset, factorVars = cat_varss, includeNA = F)
tab1

# Creating Table 2 - stratifying by functional assay status
tab1_1_tours <- CreateTableOne(vars = varss, data = raw_tours_dataset, factorVars = cat_varss, strata = c('SRAnew2'), testApprox = chisq.test, testNonNormal = T)
tab1_1_tours


# Table stratified by gender, heparin type

tab1_2 <- CreateTableOne(vars = varss, data = raw_tours_dataset, factorVars = cat_varss, strata = c('gender'), testApprox = chisq.test, testNonNormal = T)
tab1_2

tab1_2 <- CreateTableOne(vars = varss, data = raw_tours_dataset, factorVars = cat_varss, strata = c('UFH'), testApprox = chisq.test, testNonNormal = T)
tab1_2

# Table subset by positive/negative OD patients only
tab2 <- CreateTableOne(vars = varss, data = subset(raw_tours_dataset, OD >= 0.5), factorVars = cat_varss)
tab2

tab3 <- CreateTableOne(vars = varss, data = subset(raw_tours_dataset, OD < 0.5), factorVars = cat_varss)
tab3

# Analysis on only funcational assay positive/negative patients
tab4 <- CreateTableOne(vars = varss, data = subset(raw_tours_dataset, SRAnew2 == 1), factorVars = cat_varss)
tab4

tab5 <- CreateTableOne(vars = varss, data = subset(raw_tours_dataset, SRAnew2 == 0), factorVars = cat_varss)
tab5

```

### Linear regression on OD and age
```{r}
lin_age_od_tours <- lm(OD ~ age, data = raw_tours_dataset)
summary(lin_age_od_tours)
exp(coef(lin_age_od_tours))

# Checking for distribution of the residuals
res <- lin_age_od_tours$residuals
res <- data.frame(res)
ggplot(data = res, aes(res)) + geom_histogram(aes(y = ..density..), binwidth = .1, color = "blue") +
  stat_function(fun = dnorm, args = list(mean = mean(res$res), sd = sd(res$res)))


# Association of age and OD - subset functional assay positive

lin_od_possra <- lm(OD ~ age, data = raw_tours_dataset, subset = raw_tours_dataset$SRAnew2 == 1)
summary(lin_od_possra)

ggplot(subset(raw_tours_dataset, SRAnew2 ==1) , aes(x = age, y = OD, color= gender, group = gender )) + geom_point() + geom_smooth(method = 'lm', formula = y ~ x)

# Subset on SRAnew2 negative


lin_od_negsra <- lm(OD ~ age, data = raw_tours_dataset, subset = raw_tours_dataset$SRAnew2 == 0)
summary(lin_od_negsra)


ggplot(subset(raw_tours_dataset, SRAnew2 ==0) , aes(x = age, y = OD, color= gender, group = gender )) + geom_point() + geom_smooth(method = 'lm', formula = y ~ x)

# Regression on IgG positive patients

lin_age_odpos_tours <- lm(OD ~ age, data = subset(raw_tours_dataset, OD > 0.5))
summary(lin_age_odpos_tours)

# Linear Regression on age, subset by sex

lin_age_od_submale_tours <- lm(OD ~ age, data = raw_tours_dataset, subset = gender == 1)
summary(lin_age_od_submale_tours)

lin_age_od_subfemale_tours <- lm(OD ~ age, data = raw_tours_dataset, subset = gender == 2)
summary(lin_age_od_subfemale_tours)

# Linear regression on age, subset by functional assay status

lin_age_od_subsrapos <- lm(OD ~ age, data = raw_tours_dataset, subset = SRAnew2 == 1)
summary(lin_age_od_subsrapos)

ggplot(subset(raw_tours_dataset, SRAnew2 == 1 ), aes(x = age, y = OD)) + geom_point() + geom_smooth(method = 'lm', formula = y ~ x, aes(col = 'lfit'))

# Functional assay negative 
lin_age_od_subsraneg <- lm(OD ~ age, data = raw_tours_dataset, subset = SRAnew2 == 0)
summary(lin_age_od_subsraneg)

ggplot(subset(raw_tours_dataset, SRAnew2 == 0 ), aes(x = age, y = OD)) + geom_point() + geom_smooth(method = 'lm', formula = y ~ x, aes(col = 'lfit'))
```

### Association of gender and OD units
```{r}
unique(raw_tours_dataset$gender)

lin_gender_od_tours <- lm(OD ~ gender, data = raw_tours_dataset)
summary(lin_gender_od_tours)

# Checking for distribution of the residuals
res <- lin_gender_od_tours$residuals
res <- data.frame(res)

# GGplot of  residuals

ggplot(data = res, aes(res)) + geom_histogram(aes(y = ..density..), binwidth = .1, color = "blue") +
  stat_function(fun = dnorm, args = list(mean = mean(res$res), sd = sd(res$res)))

g <- ggplot(data = raw_tours_dataset, aes(y = OD, x = gender, fill = gender)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
geom_point(aes(y = OD, color = gender), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
geom_boxplot(width = .1, show.legend = FALSE, outlier.shape = NA, alpha = 0.5) +
expand_limits(x = 2.5) +
guides(fill = "none") +
guides(color = "none") +
scale_color_brewer(palette = "Set1") +
scale_fill_brewer(palette = "Set1") +
coord_flip() +
theme_bw() +
raincloud_theme

g + ggtitle('Tours: Antibody levels vs. Gender') + labs(y = "Antibody Levels", x = "Gender") +scale_x_discrete(labels = c( '2' = 'Female', '1' = 'Male'))




# Optical density and gender subset SRAnew2


lin_gender_od_tours_subsra <- lm(OD ~ gender, data = raw_tours_dataset, subset = raw_tours_dataset$SRAnew2 == 1 )
summary(lin_gender_od_tours_subsra)


lin_gender_od_tours_subsraneg <- lm(OD ~ gender, data = raw_tours_dataset, subset = raw_tours_dataset$SRAnew2 == 0 )
summary(lin_gender_od_tours_subsraneg)

# IgG positive

lin_gender_igg_pos_tours <- lm(OD ~ gender, data = raw_tours_dataset, subset = raw_tours_dataset$OD > 0.5)
summary(lin_gender_igg_pos_tours)
```


### Regression on OD and Platelet count (PLT_before)
```{r}

lin_plt_od_tours <- lm(OD ~ PLT_before, data = raw_tours_dataset)
summary(lin_plt_od_tours)


ggplot(data = raw_tours_dataset, aes(x = PLT_before, y = OD)) + geom_point() + geom_smooth(method = 'lm', formula = y ~ x, aes(col = 'lfit'))


ggplot(data = raw_tours_dataset, aes(PLT_before)) + geom_histogram(aes(y = ..density..), binwidth = .04,color = "blue") +
  stat_function(fun = dnorm, args = list(mean = mean(raw_tours_dataset$PLT_before), sd = sd(raw_tours_dataset$PLT_before)))

# Subsetting the platelet before on funcational assay status

lin_plt_od_tours_subsra <- lm(OD ~ PLT_before, data = raw_tours_dataset, subset = raw_tours_dataset$SRAnew2 == 1)
summary(lin_plt_od_tours_subsra)

lin_plt_od_tours_subsraneg <- lm(OD ~ PLT_before, data = raw_tours_dataset, subset = raw_tours_dataset$SRAnew2 == 1)
summary(lin_plt_od_tours_subsraneg)

ggplot(subset(raw_tours_dataset, raw_tours_dataset$SRAnew2 == 0), aes(x = PLT_before, y = OD)) + geom_point() + geom_smooth(method = 'lm', formula = y ~ x, aes(col = 'lfit'))
```

### Regression on OD and CBP variable
```{r}
lin_cpb_od_tours <- lm(OD ~ CPBnew, data = raw_tours_dataset)
summary(lin_cpb_od_tours)

unique(raw_tours_dataset$CPBnew)

sum(is.na(raw_tours_dataset$CPBnew))

h <- ggplot(data = raw_tours_dataset, aes(y = OD, x = CPBnew, fill = CPBnew)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
geom_point(aes(y = OD, color = CPBnew), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
expand_limits(x = 2.25) +
guides(fill = FALSE) +
guides(color = FALSE) +
scale_color_brewer(palette = "Set1") +
scale_fill_brewer(palette = "Set1") +
coord_flip() +
theme_bw() +
raincloud_theme

h
```


### Regression on OD and Thrombosis
```{r}
lin_thromb_od_tours <- lm(OD ~ thrombosisnew, data = raw_tours_dataset)
summary(lin_thromb_od_tours)


# SUBset SRA positivity on od and thrombosis
lin_throm_od_subsra <- lm(OD ~ thrombosisnew, data = raw_tours_dataset, subset = raw_tours_dataset$SRAnew2 == 1)
summary(lin_throm_od_subsra)

# This CANNOT BE RAN as there is no thrombosis controls in the SRA contols subset
#lin_throm_od_subnosra <- lm(OD ~ thrombosisnew, data = raw_tours_dataset, subset = raw_tours_dataset$SRAnew2 == 0)
#summary(lin_throm_od_subnosra)
```

### Regression on UFH and OD
```{r}
lin_ufh_od_tours <- lm(OD ~ UFH, data = raw_tours_dataset)
summary(lin_ufh_od_tours)

raw_tours_demographic_subsetUFH <- raw_tours_dataset[!is.na(raw_tours_dataset$UFH),]


k <- ggplot(data = raw_tours_demographic_subsetUFH, aes(y = OD, x = UFH, fill = UFH)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
geom_point(aes(y = OD, color = UFH), position = position_jitter(width = .15), size = .5, alpha = 0.8) + geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
expand_limits(x = 2.25) +
guides(fill = FALSE) +
guides(color = FALSE) +
scale_color_brewer(palette = "Set1") +
scale_fill_brewer(palette = "Set1") +
coord_flip() +
theme_bw() +
raincloud_theme

k
```


## Logistic Regression on SRA (Functional Assay [HIT]) - Table 3
###Funcational assay  logistic regression OD
```{r}
lo_sra_od_tours <- glm(SRAnew2 ~ OD, data =  raw_tours_dataset, family = binomial(link =  'logit'))
summary(lo_sra_od_tours)
exp(coef(lo_sra_od_tours))
or_glm(raw_tours_dataset,lo_sra_od_tours, incr = list(OD = 1))

l <- ggplot(data = raw_tours_dataset, aes(y = OD, x = SRAnew2, fill = SRAnew2)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
geom_point(aes(y = OD, color = SRAnew2), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
expand_limits(x = 2) +
guides(fill = FALSE) +
guides(color = FALSE) +
scale_color_brewer(palette = "Set1") +
scale_fill_brewer(palette = "Set1") +
coord_flip() +
theme_bw() +
raincloud_theme

l
```

### Functional assay regression on age 
```{r}

class(raw_tours_dataset$SRAnew2)

lo_sra_age_tours <- glm(SRAnew2 ~ age, data = raw_tours_dataset, family = binomial(link = 'logit'))
summary(lo_sra_age_tours)

or_glm(raw_tours_dataset,lo_sra_age_tours, incr = list(age = 1))

# age on SRA for women vs. men

lo_sra_age_tours_gendersubset <- glm(SRAnew2 ~ age, data = subset(raw_tours_dataset, gender ==2), family = binomial(link = 'logit'))
summary(lo_sra_age_tours_gendersubset)
exp(coef(lo_sra_age_tours_gendersubset))

or_glm(raw_tours_dataset,lo_sra_age_tours_gendersubset, incr = list(age = 1))

m <- ggplot(data = subset(raw_tours_dataset, !is.na(raw_tours_dataset$SRAnew2)), aes(y = age, x = SRAnew2, fill = SRAnew2)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
geom_point(aes(y = age, color = SRAnew2), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
expand_limits(x = 2) +
guides(fill = FALSE) +
guides(color = FALSE) +
scale_color_brewer(palette = "Set1") +
scale_fill_brewer(palette = "Set1") +
coord_flip() +
theme_bw() +
raincloud_theme

m
```


###Funcational assay on gender
```{r}
lo_sra_gender_tours <- glm(SRAnew2 ~ gender, data = raw_tours_dataset, family =binomial(link = 'logit'))
summary(lo_sra_gender_tours)
exp(coef(lo_sra_gender_tours))
or_glm(raw_tours_dataset,lo_sra_gender_tours, incr = list(age = 1))
```


### Funcational assay and PLT_before
```{r}

lo_sra_plt_tours <- glm(SRAnew2 ~ PLT_before, data = raw_tours_dataset, family = binomial(link = 'logit'))
summary(lo_sra_plt_tours)
or_glm(raw_tours_dataset, lo_sra_plt_tours, incr = list(PLT_before = 1))

n <- ggplot(data = subset(raw_tours_dataset, !is.na(raw_tours_dataset$SRAnew2)), aes(y = PLT_before, x = SRAnew2, fill = SRAnew2)) +
geom_flat_violin(position = position_nudge(x = .2, y = 0), alpha = .8) +
geom_point(aes(y = PLT_before, color = SRAnew2), position = position_jitter(width = .15), size = .5, alpha = 0.8) +
geom_boxplot(width = .1, guides = FALSE, outlier.shape = NA, alpha = 0.5) +
expand_limits(x = 2) +
guides(fill = FALSE) +
guides(color = FALSE) +
scale_color_brewer(palette = "Set1") +
scale_fill_brewer(palette = "Set1") +
coord_flip() +
theme_bw() +
raincloud_theme

n
```


### Funcational assay regression on unfractionated Heparin
```{r}
lo_sra_ufh_tours <- glm(SRAnew2 ~ UFH, data = raw_tours_dataset, family = binomial(link = 'logit'))
summary(lo_sra_ufh_tours)
exp(coef(lo_sra_ufh_tours))
or_glm(raw_tours_dataset, lo_sra_ufh_tours)


summary(raw_tours_dataset$UFH)
```


### Logistic regression on SRA and surgery
```{r}
lo_sra_surgery_tours <- glm(SRAnew2 ~ CPBnew, data = raw_tours_dataset, family = binomial(link = 'logit'))
summary(lo_sra_surgery_tours)
exp(coef(lo_sra_surgery_tours))
or_glm(raw_tours_dataset, lo_sra_surgery_tours)
# did not converge....
```


## Stepwise backwards regression modeling, Youden's J - Table 4

```{r}


tours_demographic_naomit <- filter(raw_tours_dataset, !is.na(OD) & !is.na(age) & !is.na(gender) & !is.na(PLT_before) & !is.na(SRAnew2))

fit1_tours <- glm(data = tours_demographic_naomit, SRAnew2 ~ OD + age + gender + PLT_before, family = binomial(link = 'logit') )
# stepwise regression model

step_model_tours <- fit1_tours %>% stepAIC(trace = T)
#summary of the output
summary(step_model_tours)
coef(step_model_tours)

exp(coef(step_model_tours))

exp(confint(step_model_tours))
or_glm(tours_demographic_naomit, step_model_tours, incr = list(OD = 1))
# Variance inflation factor aka collinearity 
car::vif(step_model_tours)

# Youden's for SRA prediction using backwards regression variables (retained)
raw_tours_dataset_backwards_df <- filter(raw_tours_dataset, !is.na(OD) & !is.na(gender) & !is.na(SRAnew2))

fit2_tours <- glm(data = raw_tours_dataset_backwards_df, SRAnew2 ~ OD + gender , family = binomial(link = 'logit'))
?predict
forward_step_preds_tours <- predict(fit2_tours)

raw_tours_dataset_backwards_df$predictor_stepwise <- forward_step_preds_tours
raw_tours_dataset_backwards_df$outcome_stepwise <- raw_tours_dataset_backwards_df$SRAnew2

cut_youdens_stepwise_tours <- cutpointr(raw_tours_dataset_backwards_df, predictor_stepwise, outcome_stepwise, method = maximize_metric, metric = youden, na.rm = T)

summary(cut_youdens_stepwise_tours)

# Plotting 

plot_metric(cut_youdens_stepwise_tours)

# Youden's for SRA prediction with just IgG variable

fit3_tours <- glm(data = raw_tours_dataset_backwards_df, SRAnew2 ~ OD, family = binomial(link = 'logit'))

forward_step_igg_toursf <- predict(fit3_tours)

raw_tours_dataset_backwards_df$predictor_igg_stepwise <- forward_step_igg_toursf
raw_tours_dataset_backwards_df$outcome_stepwise <- raw_tours_dataset_backwards_df$SRAnew2

cut_youdens_igg_tours <- cutpointr(raw_tours_dataset_backwards_df, predictor_igg_stepwise, outcome_stepwise, method = maximize_metric, metric = youden, na.rm = T)

summary(cut_youdens_igg_tours)


# COMPARING IF THE FULL MODEL DOES BETTER AT PREDICTION VS. JUST ANTIBODY ALONE

reg_sra_igg_tours <- glm(data = tours_demographic_naomit, SRAnew2 ~ OD, family = binomial(link = 'logit'))
stepwise_reg_model_tours <- glm(data = tours_demographic_naomit, SRAnew2 ~ OD + gender, family = binomial(link = 'logit'))

lr.test(stepwise_reg_model_tours, reg_sra_igg_tours)

lmtest::lrtest(stepwise_reg_model_tours, reg_sra_igg_tours)

AIC(stepwise_reg_model_tours, reg_sra_igg_tours)

# Comparing AUC of full model vs OD
auc(raw_tours_dataset_backwards_df$SRAnew2, raw_tours_dataset_backwards_df$predictor_stepwise)
auc(raw_tours_dataset_backwards_df$SRAnew2, raw_tours_dataset_backwards_df$OD)


```


## Youdens J and ROC for best dichotimizing for IgG and HIPA - Table 5

```{r}
# creating subset dataframe for only necessary variables

# select only variable needed for cut points

optimal_cut_youdens_tours_df <- raw_tours_dataset %>% dplyr::select(OD, SRAnew2, gender)

tours_optimal_cut_df <- optimal_cut_youdens_tours_df %>% dplyr::select(predictor = OD, outcome = SRAnew2) %>% mutate(cohort = 'Tours')

class(tours_optimal_cut_df)

tours_optimal_cut_df <- as.data.frame(tours_optimal_cut_df)

class(tours_optimal_cut_df)

# Running cutpointr to find optimal cutpoint 
cut_youdens_grief <- cutpointr(tours_optimal_cut_df, predictor, outcome, method = maximize_metric, metric = youden, na.rm = T)

summary(cut_youdens_grief)
plg <- plot_metric(cut_youdens_grief)

plg + ggtitle('Grief - Antibody Cutpoint for HIT Determination') + theme_minimal()

# Manual Cutpoints

optimal_cut_youdens_tours_df$predictor <- optimal_cut_youdens_tours_df$OD
optimal_cut_youdens_tours_df$outcome <- optimal_cut_youdens_tours_df$SRAnew2

cut_youdens_manual_0.4 <- cutpointr(tours_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 0.4, na.rm = T)

summary(cut_youdens_manual_0.4)


cut_youdens_manual_1.0 <- cutpointr(tours_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 1.0, na.rm = T)

summary(cut_youdens_manual_1.0)

cut_youdens_manual_1.5 <- cutpointr(tours_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 1.5, na.rm = T)

summary(cut_youdens_manual_1.5)

cut_youdens_manual_2.0 <- cutpointr(tours_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 2.0, na.rm = T)

summary(cut_youdens_manual_2.0)

cut_youdens_manual_2.5 <- cutpointr(tours_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 2.5, na.rm = T)

summary(cut_youdens_manual_2.5)

cut_youdens_manual_3.0 <- cutpointr(tours_optimal_cut_df, predictor, outcome, cohort, method = oc_manual, cutpoint = 3.0, na.rm = T)

summary(cut_youdens_manual_3.0)

```


## Including OD, age and gender (common variables in all 3 cohorts)

```{r}
reg_sra_od_age_gender_tours <- glm(SRAnew2 ~ OD + age + gender, data = raw_tours_dataset, family = binomial(link = 'logit'))

summary(reg_sra_od_age_gender_tours)
exp(coef(reg_sra_od_age_gender_tours))
or_glm(raw_tours_dataset, reg_sra_od_age_gender_tours, incr = list(OD = 1, age = 1))
```
